---
title: "Bootstrap2"
author: "Marion Boisseaux"
date: "2026-02-02"
output: html_document
---
---
title: "Bootstrap"
output: html_document
date: "2025-06-10"
editor_options: 
  chunk_output_type: console
---

##Notes

The script uses a function called *mybootPX* which is adapted from Gavin's R package *hydrafit* for estimating parameters for functions of plant hydraulic vulnerability : https://github.com/brownegm/hydrafit

*boot_vals* = distribution of all P50 values recalculated. 

*boot_mean* = mean of bootstrap values, which can be biased by the distribution queue

*boot_median* = median of bootstrap values (usually more robust).

*boot_se* = standard error of bootstrap values, estimator uncertainty

*margin_error* = t_score × boot_se, width of confidence interval (95%).

*conf.low / conf.high* = confidence interval around the "observed value", value from the best fit model.


#Library
```{r}
devtools::install_github("brownegm/hydrafit", force= T)
install.packages("here")
knitr::opts_knit$set(root.dir = "C:/Users/mboisse/Dropbox/Mon PC (Jaboty20)/Post_doc_CalState_LA/Miquel_data")

library(hydrafit)
library(ggplot2)
library(agricolae)
library(plyr)
library(multcomp)
library(corrplot)
library(factoextra)
library(readxl)
library(dplyr)
library(ggpubr)
library(cowplot)
library(tidyr)
library(readr)
library(stringr)
library(tibble)
library(purrr)
library(readr)
library(FSA)

result_path <- "C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Post_doc_CalState_LA/Miquel_data/results"
```


# Functions

## converstion

```{r}
se <- function(x, na.rm = T){
  sd(x, na.rm = na.rm)/sqrt(length(x))
}

#Convert function to Marvin/Hydrafit structure in order to use the BootPX function

convert <- function(fit) {

  mod_code <- unname(model_map[fit$model])

  out <- list(
    species = fit$Species,
    data.type = mod_code,

    A = fit$A,
    B = fit$B,
    C = fit$C,
    D = if (!is.null(fit$D)) fit$D else NA,

    loglikeli = fit$loglikeli,
    rsq = fit$rsq,
    slope = fit$slope,
    AIC = fit$AIC,
    AICcorr = fit$AICcorr,

    sterrorA = fit$sterrorA,
    sterrorB = fit$sterrorB,
    sterrorC = fit$sterrorC,
    sterrorD = fit$sterrorD,

    N = fit$N,

    maxCond = fit$Kmax,
    psi_k20 = fit$psi_kleaf20,
    psi_k50 = fit$psi_kleaf50,
    psi_k80 = fit$psi_kleaf80,
    psi_k95 = fit$psi_kleaf95,

    max_cond_at0.1 = fit$Kmax_at_0.1MPa,
    psi_k20_at0.1 = fit$psi_kleaf20,
    psi_k50_at0.1 = fit$psi_kleaf50,
    psi_k80_at0.1 = fit$psi_kleaf80,
    psi_k95_at0.1 = fit$psi_kleaf95,
    
    vcov = fit$vcov,

    plot = NULL,
    models_within_2AIC = NA
  )

  attr(out, "mod.type") <- mod_code
  attr(out, "fit.list") <- FALSE

  return(out)
}
```

#Assimilation - A
```{r}
# Load all model fitting results (RDS file containing previously computed model fits). This is done using the following script: "Script for curve fit - AIC and parameters-Boisseaux/Browne
all_results_r <- readRDS("../results/A/A_anneal_modified/model_fitting_results_full_A.RDS") 

# Select the specific subset of models corresponding to sigmoid fits for Assimilation
marion <- c(all_results_r[4], all_results_r[9], all_results_r[14], all_results_r[19], all_results_r[24], all_results_r[29])

##Convert Marion's model structure into Hydrafit format for each species
avsa_fit <- convert_marion_to_best(marion$Avsa_1_Sigmoidal)
hovu_fit <- convert_marion_to_best(marion$Hovu_1_Sigmoidal)
trae_fit <- convert_marion_to_best(marion$Trae_1_Sigmoidal)
chga_fit <- convert_marion_to_best(marion$Chga_1_Sigmoidal)
pegl_fit <- convert_marion_to_best(marion$Pegl_1_Sigmoidal)
zema_fit <- convert_marion_to_best(marion$Zema_1_Sigmoidal)

# Perform bootstrap analysis
avsa_boot <- bootPX(fit = avsa_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
hovu_boot <- bootPX(fit = hovu_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
trae_boot <- bootPX(fit = trae_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

chga_boot <- bootPX(fit = chga_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
pegl_boot <- bootPX(fit = pegl_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
zema_boot <- bootPX(fit = zema_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

# Combine all bootstrap results into a single list for easier handling
boot_list <- list(
  avsa = avsa_boot,
  hovu = hovu_boot,
  trae = trae_boot,
  chga = chga_boot,
  pegl = pegl_boot,
  zema = zema_boot)

# Define which species are C3 and which are C4
c3_species <- c("avsa", "hovu", "trae")
c4_species <- c("chga", "pegl", "zema")


# Create a tidy table from the bootstrap Assimilation results for all species
boot_table_A <- purrr::map_dfr(names(boot_list), function(name) {
  x <- boot_list[[name]]
  tibble::tibble(
    Species = x$species,
    type = if (tolower(name) %in% c3_species) "C3" else "C4",
    psi_PX = x$psi_PX,
    boot_mean = x$boot_mean,
    boot_median = x$boot_median,
    boot_se = x$boot_se,
    margin_error = x$margin_error,
    px_est = x$px_est,
    conf.low = x$conf.low,
    conf.high = x$conf.high)})

boot_table_A

# Save the bootstrap summary table to a CSV file
write.csv(x = boot_table_A, file = "../results/A/boottableA.csv")
```

#Conductance - gs
```{r}
# Load all model fitting results (RDS file containing previously computed model fits). This is done using the following script: "Script for curve fit - AIC and parameters-Boisseaux/Browne
all_results_r <- readRDS("../results/gs/gs_anneal_modified/model_fitting_results_full_gs.RDS") 

# Select the specific subset of models corresponding to X fits for Stomatal conductance (gs)
marion <- c(all_results_r[4], all_results_r[9], all_results_r[14], all_results_r[19], all_results_r[24], all_results_r[30])

##Convert Marion's model structure into Hydrafit format for each species
avsa_fit <- convert_marion_to_best(marion$Avsa_1_Sigmoidal)
hovu_fit <- convert_marion_to_best(marion$Hovu_1_Sigmoidal)
trae_fit <- convert_marion_to_best(marion$Trae_1_Sigmoidal)
chga_fit <- convert_marion_to_best(marion$Chga_1_Sigmoidal)
pegl_fit <- convert_marion_to_best(marion$Pegl_1_Sigmoidal)
zema_fit <- convert_marion_to_best(marion$Zema_1_Linear)

# Perform bootstrap analysis
avsa_boot <- bootPX(fit = avsa_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
hovu_boot <- bootPX(fit = hovu_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
trae_boot <- bootPX(fit = trae_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

chga_boot <- bootPX(fit = chga_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
pegl_boot <- bootPX(fit = pegl_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
zema_boot <- bootPX(fit = zema_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

# Combine all bootstrap results into a single list for easier handling
boot_list <- list(
  avsa = avsa_boot,
  hovu = hovu_boot,
  trae = trae_boot,
  chga = chga_boot,
  pegl = pegl_boot,
  zema = zema_boot)

# Define which species are C3 and which are C4
c3_species <- c("avsa", "hovu", "trae")
c4_species <- c("chga", "pegl", "zema")


# Create a tidy table from the bootstrap results for all species
boot_table_gs <- purrr::map_dfr(names(boot_list), function(name) {
  x <- boot_list[[name]]
  tibble::tibble(
    Species = x$species,
    type = if (tolower(name) %in% c3_species) "C3" else "C4",
    psi_PX = x$psi_PX,
    boot_mean = x$boot_mean,
    boot_median = x$boot_median,
    boot_se = x$boot_se,
    margin_error = x$margin_error,
    px_est = x$px_est,
    conf.low = x$conf.low,
    conf.high = x$conf.high)})

boot_table_gs

# Save the bootstrap summary table to a CSV file
write.csv(x = boot_table_gs, file = "../results/gs/boottablegs.csv")
```

#Kleaf
```{r}
# Load all model fitting results (RDS file containing previously computed model fits). This is done using the following script: "Script for curve fit - AIC and parameters-Boisseaux/Browne
all_results_r <- readRDS("../results/Kleaf/Kleaf_anneal_modified/model_fitting_results_full_Kleaf.RDS") 

# Select the specific subset of models corresponding to X fits for Kleaf
marion <- c(all_results_r[3], all_results_r[7], all_results_r[11], all_results_r[18], all_results_r[23], all_results_r[28])

##Convert Marion's model structure into Hydrafit format for each species
avsa_fit <- convert_marion_to_best(marion$AVSA_1_Logistic)
hovu_fit <- convert_marion_to_best(marion$HOVU_1_Exponential2)
trae_fit <- convert_marion_to_best(marion$TRAE_1_Exponential)
chga_fit <- convert_marion_to_best(marion$CHGA_1_Logistic)
pegl_fit <- convert_marion_to_best(marion$PEGL_1_Logistic)
zema_fit <- convert_marion_to_best(marion$ZEMA_1_Logistic)

# Perform bootstrap analysis
avsa_boot <- bootPX(fit = avsa_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
hovu_boot <- bootPX(fit = hovu_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
trae_boot <- bootPX(fit = trae_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

chga_boot <- bootPX(fit = chga_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
pegl_boot <- bootPX(fit = pegl_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
zema_boot <- bootPX(fit = zema_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

# Combine all bootstrap results into a single list for easier handling
boot_list <- list(
  avsa = avsa_boot,
  hovu = hovu_boot,
  trae = trae_boot,
  chga = chga_boot,
  pegl = pegl_boot,
  zema = zema_boot)

# Define which species are C3 and which are C4
c3_species <- c("avsa", "hovu", "trae")
c4_species <- c("chga", "pegl", "zema")


# Create a tidy table from the bootstrap results for all species
boot_table_Kleaf <- purrr::map_dfr(names(boot_list), function(name) {
  x <- boot_list[[name]]
  tibble::tibble(
    Species = x$species,
    type = if (tolower(name) %in% c3_species) "C3" else "C4",
    psi_PX = x$psi_PX,
    boot_mean = x$boot_mean,
    boot_median = x$boot_median,
    boot_se = x$boot_se,
    margin_error = x$margin_error,
    px_est = x$px_est,
    conf.low = x$conf.low,
    conf.high = x$conf.high)})

boot_table_Kleaf

# Save the bootstrap summary table to a CSV file
write.csv(x = boot_table_Kleaf, file = "../results/Kleaf/boottableKleaf.csv")
```

#Kplant
```{r}
# Load all model fitting results (RDS file containing previously computed model fits). This is done using the following script: "Script for curve fit - AIC and parameters-Boisseaux/Browne
all_results_r <- readRDS("../results/KplantKroots_results/Kplant/Kplant_anneal_modified/model_fitting_results_full_Kplant.RDS") 

# Select the specific subset of models corresponding to X fits for Kplant
marion <- c(all_results_r[1], all_results_r[9], all_results_r[14], all_results_r[16], all_results_r[25], all_results_r[26])

##Convert Marion's model structure into Hydrafit format for each species
avsa_fit <- convert_marion_to_best(marion$AVSA_1_Exponential)
hovu_fit <- convert_marion_to_best(marion$HOVU_1_Sigmoidal)
trae_fit <- convert_marion_to_best(marion$TRAE_1_Sigmoidal)
chga_fit <- convert_marion_to_best(marion$CHGA_1_Exponential)
pegl_fit <- convert_marion_to_best(marion$PEGL_1_Exponential)
zema_fit <- convert_marion_to_best(marion$ZEMA_1_Linear)

# Perform bootstrap analysis
avsa_boot <- bootPX(fit = avsa_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
hovu_boot <- bootPX(fit = hovu_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
trae_boot <- bootPX(fit = trae_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

chga_boot <- bootPX(fit = chga_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
pegl_boot <- bootPX(fit = pegl_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
zema_boot <- bootPX(fit = zema_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

# Combine all bootstrap results into a single list for easier handling
boot_list <- list(
  avsa = avsa_boot,
  hovu = hovu_boot,
  trae = trae_boot,
  chga = chga_boot,
  pegl = pegl_boot,
  zema = zema_boot)

# Define which species are C3 and which are C4
c3_species <- c("avsa", "hovu", "trae")
c4_species <- c("chga", "pegl", "zema")


# Create a tidy table from the bootstrap results for all species
boot_table_Kplant <- purrr::map_dfr(names(boot_list), function(name) {
  x <- boot_list[[name]]
  tibble::tibble(
    Species = x$species,
    type = if (tolower(name) %in% c3_species) "C3" else "C4",
    psi_PX = x$psi_PX,
    boot_mean = x$boot_mean,
    boot_median = x$boot_median,
    boot_se = x$boot_se,
    margin_error = x$margin_error,
    px_est = x$px_est,
    conf.low = x$conf.low,
    conf.high = x$conf.high)})

boot_table_Kplant

# Save the bootstrap summary table to a CSV file
write.csv(x = boot_table_Kplant, file = "../results/KplantKroots_results/Kplant/boottableKplant.csv")
```

#Kroot

```{r}
# Load all model fitting results (RDS file containing previously computed model fits). This is done using the following script: "Script for curve fit - AIC and parameters-Boisseaux/Browne
all_results_r <- readRDS("../results/KplantKroots_results/Kroot/Kroot_anneal_modified/model_fitting_results_full_Kroot.RDS") 

# Select the specific subset of models corresponding to X fits for Kroot
marion <- c(all_results_r[1], all_results_r[6], all_results_r[12], all_results_r[16], all_results_r[21], all_results_r[26])

##Convert Marion's model structure into Hydrafit format for each species
avsa_fit <- convert_marion_to_best(marion$AVSA_1_Exponential)
hovu_fit <- convert_marion_to_best(marion$HOVU_1_Exponential)
trae_fit <- convert_marion_to_best(marion$TRAE_1_Exponential2)
chga_fit <- convert_marion_to_best(marion$CHGA_1_Exponential)
pegl_fit <- convert_marion_to_best(marion$PEGL_1_Exponential)
zema_fit <- convert_marion_to_best(marion$ZEMA_1_Exponential)

# Perform bootstrap analysis
avsa_boot <- bootPX(fit = avsa_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
hovu_boot <- bootPX(fit = hovu_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
trae_boot <- bootPX(fit = trae_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

chga_boot <- bootPX(fit = chga_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
pegl_boot <- bootPX(fit = pegl_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)
zema_boot <- bootPX(fit = zema_fit, px = 0.5, psi_max = 0.1, sims = 1000, seed = 123,  margin = "quantile",  pairwise = FALSE)

# Combine all bootstrap results into a single list for easier handling
boot_list <- list(
  avsa = avsa_boot,
  hovu = hovu_boot,
  trae = trae_boot,
  chga = chga_boot,
  pegl = pegl_boot,
  zema = zema_boot)

# Define which species are C3 and which are C4
c3_species <- c("avsa", "hovu", "trae")
c4_species <- c("chga", "pegl", "zema")


# Create a tidy table from the bootstrap results for all species
boot_table_Kroot <- purrr::map_dfr(names(boot_list), function(name) {
  x <- boot_list[[name]]
  tibble::tibble(
    Species = x$species,
    type = if (tolower(name) %in% c3_species) "C3" else "C4",
    psi_PX = x$psi_PX,
    boot_mean = x$boot_mean,
    boot_median = x$boot_median,
    boot_se = x$boot_se,
    margin_error = x$margin_error,
    px_est = x$px_est,
    conf.low = x$conf.low,
    conf.high = x$conf.high)})

boot_table_Kroot

# Save the bootstrap summary table to a CSV file
write.csv(x = boot_table_Kroot, file = "../results/KplantKroots_results/Kroot/boottableKroot.csv")
```

#Combine
```{r}
boot_table_A <- boot_table_A %>% mutate(trait = "A")
boot_table_gs <- boot_table_gs %>% mutate(trait = "gs")

boot_temp <- rbind(boot_table_A, boot_table_gs)

boot_temp <- boot_temp %>%
  mutate(Species_name = case_when(
    Species == "Zema" ~ "Z. mays",
    Species == "Chga" ~ "C. gayan",
    Species == "Pegl" ~ "P. glaucum",
    Species == "Avsa" ~ "A. sativa",
    Species == "Hovu" ~ "H. vulgare",
    Species == "Trae" ~ "T. aestivum",
    TRUE ~ Species))

boot_table_Kleaf <- boot_table_Kleaf %>% mutate(trait = "Kleaf")
boot_table_Kplant <- boot_table_Kplant %>% mutate(trait = "Kplant")
boot_table_Kroot <- boot_table_Kroot %>% mutate(trait = "Kroot")

boot_temp2 <- rbind(boot_table_Kleaf, boot_table_Kroot, boot_table_Kplant)

boot_temp2 <- boot_temp2 %>%
  mutate(Species_name = case_when(
    Species == "ZEMA" ~ "Z. mays",
    Species == "CHGA" ~ "C. gayan",
    Species == "PEGL" ~ "P. glaucum",
    Species == "AVSA" ~ "A. sativa",
    Species == "HOVU" ~ "H. vulgare",
    Species == "TRAE" ~ "T. aestivum",
    TRUE ~ Species))

boottable_final <-rbind(boot_temp, boot_temp2)
boottable_final
View(boottable_final)

trait_labels <- c(
  "A"      = "P[A50]",
  "gs"     = "P[italic(g[s])*50]",
  "Kleaf"  = "P[italic(K[leaf])*50]",
  "Kplant" = "P[italic(K[plant])*50]",
  "Kroot"  = "P[italic(K[root])*50]"
)


# Remettre dans l'ordre
boottable_final$Species_name <- factor(boottable_final$Species_name,
  levels = c("Z. mays", "P. glaucum", "C. gayan", "T. aestivum", "H. vulgare", "A. sativa"))

p_trait <- boottable_final%>%
  ggplot(aes(x=Species_name, y=boot_mean, ymin=conf.low, ymax=conf.high, color=type)) +
  geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  facet_wrap(~trait, ncol=2, scales="free_x", labeller = labeller(trait = as_labeller(trait_labels, label_parsed)))+
  coord_flip() +
  labs(y="P50 (-MPa)", x="", color="Mecanism") +
  scale_color_manual(values = c("C4"="#E69F00", "C3"="#56B4E9")) +
  theme_bw(base_size=14)+
  theme(
    axis.text.y = element_text(face= "italic"),
    strip.background = element_blank(),
    legend.position = "bottom"
  )
p_trait

ggsave(filename = "../results/bootstrap.jpg", plot = p_trait, width = 6, height = 8)

```

```{r}
# Reorder species factor
boottable_final$Species_name <- factor(boottable_final$Species_name,
  levels = c("Z. mays", "P. glaucum", "C. gayan", "T. aestivum", "H. vulgare", "A. sativa"))

# Plot for trait A
 p_A <- ggplot(
  boottable_final[boottable_final$trait == "A", ],
  aes(x = Species_name, y=boot_mean,
      ymin = conf.low, ymax = conf.high,
      color = type)) +
  geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  coord_flip() +
  labs(y = "P50 (-MPa)", x = "",
       color = "Metabolism",
       title = expression(P[A50])) +
  scale_color_manual(values = c("C4" = "#E69F00", "C3" = "#56B4E9")) +
  theme_bw(base_size = 14) +
  theme(axis.text.y = element_text(face = "italic"),
        plot.title = element_text(hjust = 0),
        legend.position = "bottom")


# Plot for trait gs
p_gs <- ggplot(boottable_final[boottable_final$trait == "gs", ],
              aes(x = Species_name,y=boot_mean,
      ymin = conf.low, ymax = conf.high,
      color = type)) +
 geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  coord_flip() +
  labs(y = "P50 (-MPa)", x = "",
       color = "Metabolism",
      title = expression(P[italic(g[s])*50])) +
  scale_color_manual(values = c("C4" = "#E69F00", "C3" = "#56B4E9")) +
  theme_bw(base_size = 14) +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0),
        legend.position = "bottom")

# Plot for trait Kleaf
p_Kleaf <- ggplot(boottable_final[boottable_final$trait == "Kleaf", ],
                  aes(x = Species_name,y=boot_mean,
      ymin = conf.low, ymax = conf.high,
      color = type)) +
 geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  coord_flip() +
  labs(y = "P50 (-MPa)", x = "",
       color = "Metabolism",
       title = expression(P[italic(K[leaf])*50])) +
  scale_color_manual(values = c("C4" = "#E69F00", "C3" = "#56B4E9")) +
  theme_bw(base_size = 14) +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0),
        legend.position = "bottom")

# Plot for trait Kplant
p_Kplant <- ggplot(boottable_final[boottable_final$trait == "Kplant", ],
                 aes(x = Species_name,y=boot_mean,
      ymin = conf.low, ymax = conf.high,
      color = type)) +
  geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  coord_flip() +
  labs(y = "P50 (-MPa)", x = "",
       color = "Metabolism",
       title = expression(P[italic(K[plant])*50])) +
  scale_color_manual(values = c("C4" = "#E69F00", "C3" = "#56B4E9")) +
  theme_bw(base_size = 14) +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0),
        legend.position = "bottom")

# Plot for trait Kroot
p_Kroot <- ggplot(boottable_final[boottable_final$trait == "Kroot", ],
                  aes(x = Species_name,y=boot_mean,
      ymin = conf.low, ymax = conf.high,
      color = type)) +
  geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  coord_flip() +
  labs(y = "P50 (-MPa)", x = "",
       color = "Metabolism",
       title = expression(P[italic(K[root])*50])) +
  scale_color_manual(values = c("C4" = "#E69F00", "C3" = "#56B4E9")) +
  theme_bw(base_size = 14) +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0),
        legend.position = "bottom")

Figure2 <- ggarrange(p_A, p_gs, p_Kleaf, p_Kplant, p_Kroot, labels = c("A", "B", "C", "D", "E", "F"),heights = c(1,1,1,1,1) , widths = c(1.38, 1, 1, 1, 1), ncol = 5, nrow = 1, common.legend = TRUE, legend = "bottom")

Figure2 
ggsave(filename = "../results/Figure_bootstrap2.jpg", plot = Figure2, width = 12, height = 4)

```

#Compare traits within a given species

```{r}

boottable_final <- boottable_final %>%
  mutate(trait_label = case_when(
    trait == "A" ~ "A",
    trait == "gs" ~ "g[s]",
    trait == "Kleaf" ~ "K[leaf]",
    trait == "Kplant" ~ "K[plant]",
    trait == "Kroot" ~ "K[root]",
    TRUE ~ trait))

boottable_final <- boottable_final %>%
  mutate(Species_label = case_when(
    Species_name == "Z. mays"     ~ "italic('Z. mays')",
    Species_name == "C. gayan"    ~ "italic('C. gayan')",
    Species_name == "P. glaucum"  ~ "italic('P. glaucum')",
    Species_name == "A. sativa"   ~ "italic('A. sativa')",
    Species_name == "H. vulgare"  ~ "italic('H. vulgare')",
    Species_name == "T. aestivum" ~ "italic('T. aestivum')",
    TRUE ~ Species_name
  ))


boottable_final$trait_label <- factor(boottable_final$trait_label,
  levels = c("A","g[s]", "K[plant]", "K[leaf]", "K[root]"))

p_species <- boottable_final %>%
  ggplot(aes(x=trait_label, y=px_est, ymin=conf.low, ymax=conf.high, color=type)) +
  geom_pointrange(position=position_dodge(width=0.5), size=0.8) +
  facet_wrap(~Species_label, ncol=2, scales="free_x", labeller=label_parsed)+ 
  coord_flip() +
  labs(y="P50 (-MPa)", x="", color="Mecanism") +
  scale_color_manual(values = c("C4"="#E69F00", "C3"="#56B4E9")) +
  scale_x_discrete(labels = c(
  "A" = expression(A),
  "g[s]" = expression(g[s]),
  "K[plant]" = expression(K[plant]),
  "K[leaf]" = expression(K[leaf]),
  "K[root]" = expression(K[root])
))+
  theme_bw(base_size=14)+
  theme(
    strip.background = element_blank()
  )
p_species

ggsave(filename = "../results/boot_species.jpg",  plot = p_trait, width = 6, height = 8)
```
