---
title: "Script Marion Analyses"
author: "Marion Boisseaux"
date: "2025-01-14"
output: html_document
---

C3C4 Grasses CALSTATE LA 

#libraries 

```{r}
library(ggplot2)
library(agricolae)
library(plyr)
library(multcomp)
library(corrplot)
library(factoextra)
library(readxl)
library(dplyr)
library(ggpubr)
library(cowplot)
```

#Leaf dehydration and recovery assay

##data 
SRC, data loading, variable calculation, outliers, means 
```{r}
SRCdata <- read_xlsx(path = "../data/C3C4 Grasses - OV monitoring, SRC.xlsx", sheet = "C3C4G SRC") 

```

##variable calculations
```{r}
SRCdata$Metabolism<-factor(SRCdata$Metabolism)
SRCdata$Species<-factor(SRCdata$Species,levels=c("Avsa","Hovu","Trae","Pegl","Zema","Chga"))

# variable calculation
#T for initial, fully hydrated or turgid -- STAGE 1
#F for after dehydration or fresh -- STAGE 2
#R for Rehydration -- STAGE 3
#D for dry -- STAGE 4

#leaf thickness average
SRCdata$T.LT<-rowMeans(SRCdata[c("T.LT1","T.LT2","T.LT3","T.LT4","T.LT5","T.LT6")],na.rm=T) #stage 1
SRCdata$F.LT2 <- as.numeric(SRCdata$F.LT2)
SRCdata$F.LT<-rowMeans(SRCdata[c("F.LT1","F.LT2","F.LT3","F.LT4","F.LT5","F.LT6")],na.rm=T) #stage 2
SRCdata$D.LT2 <- as.numeric(SRCdata$D.LT2)
SRCdata$D.LT<-rowMeans(SRCdata[c("D.LT1","D.LT2","D.LT3","D.LT4","D.LT5","D.LT6")],na.rm=T) #stage 4

#leaf width average
SRCdata$F.LW1 <- as.numeric(SRCdata$F.LW1)
SRCdata$F.LW2 <- as.numeric(SRCdata$F.LW2)
SRCdata$F.LW3 <- as.numeric(SRCdata$F.LW3)
SRCdata$F.LW4 <- as.numeric(SRCdata$F.LW4)
SRCdata$F.LW5 <- as.numeric(SRCdata$F.LW5)

SRCdata$T.LW1<-rowMeans(SRCdata[c("T.LW1","T.LW2","T.LW3")],na.rm=T) #stage 1 - middle
SRCdata$F.LW1<-rowMeans(SRCdata[c("F.LW1","F.LW2","F.LW3")],na.rm=T) #stage 2
SRCdata$T.LW2<-rowMeans(SRCdata[c("T.LW1","T.LW4","T.LW5")],na.rm=T) #stage 1 - base
SRCdata$F.LW2<-rowMeans(SRCdata[c("F.LW1","F.LW4","F.LW5")],na.rm=T) #stage 2

SRCdata$D.LW1 <- as.numeric(SRCdata$D.LW1)
SRCdata$D.LW2 <- as.numeric(SRCdata$D.LW2)
SRCdata$D.LW3 <- as.numeric(SRCdata$D.LW3)
SRCdata$D.LW4 <- as.numeric(SRCdata$D.LW4)
SRCdata$D.LW5 <- as.numeric(SRCdata$D.LW5)

SRCdata$D.LW<-rowMeans(SRCdata[c("D.LW1","D.LW2","D.LW3","D.LW4","D.LW5")],na.rm=T) #stage 4

#Leaf volume 
SRCdata$F.LA <- as.numeric(SRCdata$F.LA)
SRCdata$D.LA <- as.numeric(SRCdata$D.LA)

SRCdata$T.LV<-SRCdata$T.LA*SRCdata$T.LT/10 #stage 1
SRCdata$F.LV<-SRCdata$F.LA*SRCdata$F.LT/10 #stage 2
SRCdata$D.LV<-SRCdata$D.LA*SRCdata$D.LT/10  #stage 4

```

#PLX : Leaf percentage loss of X variable
```{r}

#Leaf percentage loss during dehydration: thickness
SRCdata$F.PLT<-100-SRCdata$F.LT/SRCdata$T.LT*100 #stage 2 leaf thickness compared to stage 1 leaf thickness
SRCdata$D.PLT<-100-SRCdata$D.LT/SRCdata$T.LT*100 #stage 4 dry leaf thickness compared to stage 4 

#Leaf percentage loss during dehydration: leaf area
SRCdata$F.PLA<-100-SRCdata$F.LA/SRCdata$T.LA*100
SRCdata$D.PLA<-100-SRCdata$D.LA/SRCdata$T.LA*100

#Leaf percentage loss during dehydration: leaf width
SRCdata$F.PLW1<-100-SRCdata$F.LW1/SRCdata$T.LW1*100
SRCdata$D.PLW1<-100-SRCdata$D.LW/SRCdata$T.LW1*100

#Leaf percentage loss during dehydration: leaf length
SRCdata$F.LLe <- as.numeric(SRCdata$F.LLe)
SRCdata$T.LLe <- as.numeric(SRCdata$T.LLe)
SRCdata$D.LLe <- as.numeric(SRCdata$D.LLe)
SRCdata$F.PLLe<-100-SRCdata$F.LLe/SRCdata$T.LLe*100
SRCdata$D.PLLe<-100-SRCdata$D.LLe/SRCdata$T.LLe*100

##Leaf percentage loss during dehydration: leaf volume
SRCdata$F.PLV<-100-SRCdata$F.LV/SRCdata$T.LV*100
SRCdata$D.PLV<-100-SRCdata$D.LV/SRCdata$T.LV*100

```

#RWC calculations & other variables
```{r}
#RWC calculations
SRCdata$T.SWC<-(SRCdata$TW-SRCdata$DW)/SRCdata$DW
SRCdata$F.SWC<-(SRCdata$FW-SRCdata$DW)/SRCdata$DW
SRCdata$R.SWC<-(SRCdata$RW-SRCdata$DW)/SRCdata$DW
SRCdata$F.RWC<-(SRCdata$FW-SRCdata$DW)/(SRCdata$TW-SRCdata$DW)*100

#??
SRCdata$F.1_LWi.LWhy<-1-SRCdata$FW/SRCdata$TW #???

#LMA, leaf density, LDMC, 
SRCdata$LMA<-SRCdata$DW/1000/(SRCdata$T.LA/10000)
SRCdata$LD<-SRCdata$DW/1000/SRCdata$T.LV
SRCdata$LDMC<-SRCdata$DW/SRCdata$TW

#Rehydration capacity PLRC = 100- LW_rehy / LW_full saturation *100
#what the leaf recovers compared to its full turgid capacity
SRCdata$PLRC<-100-SRCdata$R.SWC/SRCdata$T.SWC*100
```

# SRC, outliers

```{r}
# PLRC of -20% 
#SRCdata$Species[!SRCdata$PLRC>-20] (Chga and Hovu)
SRCdata$PLRC[!SRCdata$PLRC>-20]<-NA #why input NA for the two values: -23.9 and -21.5?

```

#Species 
## AVSA

Question; what's the justification to put NAs for ex. Leaf 22 column 5 though 84 ??? 
```{r}
# Avsa
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==17,5:84]<-NA
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==20,5:84]<-NA
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==21,5:84]<-NA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==22,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==24,5:84]<-NA
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==25,5:84]<-NA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==26,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==29,5:84]<-NA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==30,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==31,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==32,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==43,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==44,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==45,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==46,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==47,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==49,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==51,5:84]<-NA # too small leaf (!)
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==52,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==53,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==54,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==55,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==56,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==57,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==59,5:84]<-NA # PLA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==17,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==20,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==21,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==24,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==25,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==24,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==27,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==28,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==65,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==66,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==48,70]<-NA # only D.PLA - to check photos!
```


## Chga
```{r}
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==1,5:84]<-NA # PLT - to check
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==6,5:84]<-NA # PLA - to check photos!
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==9,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==21,5:84]<-NA # PLT - to check
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==22,5:84]<-NA # LMA vs LDMC
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==24,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==25,5:84]<-NA # LMA vs LDMC
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==30,5:84]<-NA # PLT - to check
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==31,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==32,5:84]<-NA # PLRC
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==48,5:84]<-NA # FvFm
```


## Hovu
```{r}
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==3,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==4,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==5,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==6,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==7,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==8,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==15,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==17,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==19,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==49,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==50,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==56,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==55,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==14,c(69,75)]<-NA # only PLA, PLV - to check photos!
```


## Pegl 
```{r}
SRCdata[SRCdata$Species=="Pegl" & SRCdata$Leaf==35,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Pegl" & SRCdata$Leaf==38,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Pegl" & SRCdata$Leaf==42,74]<-NA # only D.PLLe - to check photos!
```


## Trae
```{r}
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==8,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==9,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==10,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==18,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==20,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==23,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==28,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==29,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==30,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==31,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==32,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==45,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==46,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==47,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==49,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==50,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==52,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==53,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==42,44]<-NA # only R FvFm - to check!
```


## Zema
```{r}
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==8,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==10,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==15,5:84]<-NA # LDMC vs LD
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==20,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==23,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==34,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==24,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==6,c(70,76)]<-NA # only DPLA, DPLV - to check photos!
```


## means 
```{r}
m.SRCdata<-ddply(SRCdata,c("Species","Metabolism"),summarise,
                m.LMA=mean(LMA,na.rm=TRUE),n.LMA=sum(!is.na(LMA)),se.LMA=sd(LMA,na.rm=T)/sqrt(n.LMA),
                m.T.LT=mean(T.LT,na.rm=TRUE),n.T.LT=sum(!is.na(T.LT)),se.T.LT=sd(T.LT,na.rm=T)/sqrt(n.T.LT),
                m.LD=mean(LD,na.rm=TRUE),n.LD=sum(!is.na(LD)),se.LD=sd(LD,na.rm=T)/sqrt(n.LD),
                m.LDMC=mean(LDMC,na.rm=TRUE),n.LDMC=sum(!is.na(LDMC)),se.LDMC=sd(LDMC,na.rm=T)/sqrt(n.LDMC),
                m.D.PLT=mean(D.PLT,na.rm=TRUE),n.D.PLT=sum(!is.na(D.PLT)),se.D.PLT=sd(D.PLT,na.rm=T)/sqrt(n.D.PLT),
                m.D.PLA=mean(D.PLA,na.rm=TRUE),n.D.PLA=sum(!is.na(D.PLA)),se.D.PLA=sd(D.PLA,na.rm=T)/sqrt(n.D.PLA),
                m.D.PLV=mean(D.PLV,na.rm=TRUE),n.D.PLV=sum(!is.na(D.PLV)),se.D.PLV=sd(D.PLV,na.rm=T)/sqrt(n.D.PLV),
                m.D.PLLe=mean(D.PLLe,na.rm=TRUE),n.D.PLLe=sum(!is.na(D.PLLe)),se.D.PLLe=sd(D.PLLe,na.rm=T)/sqrt(n.D.PLLe),
                m.D.PLW1=mean(D.PLW1,na.rm=TRUE),n.D.PLW1=sum(!is.na(D.PLW1)),se.D.PLW1=sd(D.PLW1,na.rm=T)/sqrt(n.D.PLW1))
```

#Analysis

##leaf structure
```{r}
## SRC, boxplots, stat analysis ####

# LMA
plot_LMA<-ggplot(SRCdata,aes(x=Species,y=LMA,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("LMA (g m"^-2,")")))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,50)+
  #geom_hline(yintercept=0,lty=2)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  #ylab(expression(paste("LMA (g m"^-2,")")))+
  annotate("text",x=1,y=7,label=expression(paste(italic(bar("x"))," = 31.1")),size=4)+
  annotate("text",x=1,y=4,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=7,label=expression(paste("21.2")),size=4)+
  annotate("text",x=2,y=4,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=7,label=expression(paste("27.4")),size=4)+
  annotate("text",x=3,y=4,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=7,label=expression(paste("24.7")),size=4)+
  annotate("text",x=4,y=4,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=7,label=expression(paste("20.6")),size=4)+
  annotate("text",x=5,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=7,label=expression(paste("27.5")),size=4)+
  annotate("text",x=6,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","LMA"],na.rm=T)+4,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","LMA"],na.rm=T)+4,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","LMA"],na.rm=T)+4,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","LMA"],na.rm=T)+4,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","LMA"],na.rm=T)+4,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","LMA"],na.rm=T)+4,label=expression(paste(bold("b"))),size=5)
plot_LMA

# stat
lm1<-lm(LMA~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# LT
plot_LT<-ggplot(SRCdata,aes(x=Species,y=T.LT,fill=Metabolism))+
  theme_minimal()+
  geom_boxplot(lwd=0.2,fatten=5)+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,0.4)+
  #geom_hline(yintercept=0,lty=2)+
  ggtitle("LT (mm)")+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=0.056,label=expression(paste(italic(bar("x"))," = 0.22")),size=4)+
  annotate("text",x=1,y=0.032,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=0.056,label=expression(paste("0.19")),size=4)+
  annotate("text",x=2,y=0.032,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=0.056,label=expression(paste("0.17")),size=4)+
  annotate("text",x=3,y=0.032,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=0.056,label=expression(paste("0.13")),size=4)+
  annotate("text",x=4,y=0.032,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=0.056,label=expression(paste("0.16")),size=4)+
  annotate("text",x=5,y=0.032,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=0.056,label=expression(paste("0.12")),size=4)+
  annotate("text",x=6,y=0.032,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("e"))),size=5)
plot_LT

# stat
lm1<-lm(T.LT~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# LD
plot_LD<-ggplot(SRCdata,aes(x=Species,y=LD,fill=Metabolism))+
  theme_minimal()+
  geom_boxplot(lwd=0.2,fatten=5)+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,0.4)+
  #geom_hline(yintercept=0,lty=2)+
  ggtitle(expression(paste("LD (g cm"^-3,")")))+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=0.040,label=expression(paste(italic(bar("x"))," = 0.14")),size=4)+
  annotate("text",x=1,y=0.016,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=0.040,label=expression(paste("0.11")),size=4)+
  annotate("text",x=2,y=0.016,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=0.040,label=expression(paste("0.17")),size=4)+
  annotate("text",x=3,y=0.016,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=0.040,label=expression(paste("0.19")),size=4)+
  annotate("text",x=4,y=0.016,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=0.040,label=expression(paste("0.13")),size=4)+
  annotate("text",x=5,y=0.016,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=0.040,label=expression(paste("0.24")),size=4)+
  annotate("text",x=6,y=0.016,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","LD"],na.rm=T)+0.032,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","LD"],na.rm=T)+0.032,label=expression(paste(bold("e"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","LD"],na.rm=T)+0.032,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","LD"],na.rm=T)+0.032,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","LD"],na.rm=T)+0.032,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","LD"],na.rm=T)+0.032,label=expression(paste(bold("a"))),size=5)
plot_LD

# stat
lm1<-lm(LD~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# LDMC
plot_LDMC<-ggplot(SRCdata,aes(x=Species,y=LDMC,fill=Metabolism))+
  theme_minimal()+
  geom_boxplot(lwd=0.2,fatten=5)+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,0.3)+
  #geom_hline(yintercept=0,lty=2)+
  ggtitle(expression(paste("LDMC (g g"^-1,")")))+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  #ylab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=1,y=0.024,label=expression(paste(italic(bar("x"))," = 0.13")),size=4)+
  annotate("text",x=1,y=0,label=expression(paste(italic("n")," = 44")),size=4)+
  annotate("text",x=2,y=0.024,label=expression(paste("0.11")),size=4)+
  annotate("text",x=2,y=0,label=expression(paste("47")),size=4)+
  annotate("text",x=3,y=0.024,label=expression(paste("0.16")),size=4)+
  annotate("text",x=3,y=0,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=0.024,label=expression(paste("0.11")),size=4)+
  annotate("text",x=4,y=0,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=0.024,label=expression(paste("0.10")),size=4)+
  annotate("text",x=5,y=0,label=expression(paste("41")),size=4)+
  annotate("text",x=6,y=0.024,label=expression(paste("0.16")),size=4)+
  annotate("text",x=6,y=0,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("a"))),size=5)

plot_LDMC
# stat
lm1<-lm(LDMC~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


##all graphs for leaf structure

Leaf_structure<- ggarrange(plot_LMA, plot_LT, plot_LD, plot_LDMC, ncol = 2, nrow = 2, common.legend= TRUE, legend = "bottom")
Leaf_structure

ggsave(filename = "../results/leaf_structure.jpg", plot = Leaf_structure)
```

##leaf percentage loss
```{r}
# PLTdry
PLTdry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLT,fill=Metabolism))+
   geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Thickness"["dry"]," (%)")))+
  ylim(0,100)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  #ylab()+
  annotate("text",x=1,y=10,label=expression(paste(italic(bar("x"))," = 46.1")),size=4)+
  annotate("text",x=1,y=4,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=10,label=expression(paste("69.8")),size=4)+
  annotate("text",x=2,y=4,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=10,label=expression(paste("45.8")),size=4)+
  annotate("text",x=3,y=4,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=10,label=expression(paste("56.5")),size=4)+
  annotate("text",x=4,y=4,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=10,label=expression(paste("69.2")),size=4)+
  annotate("text",x=5,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=10,label=expression(paste("46.4")),size=4)+
  annotate("text",x=6,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLT"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLT"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLT"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLT"],na.rm=T)+8,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLT"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLT"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)

PLTdry_plot
# stat
lm1<-lm(D.PLT~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# PLAdry
PLAdry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLA,fill=Metabolism))+
   geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Area"["dry"]," (%)")))+
  ylim(10,90)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=21.2,label=expression(paste(italic(bar("x"))," = 49.4")),size=4)+
  annotate("text",x=1,y=16.4,label=expression(paste(italic("n")," = 48")),size=4)+
  annotate("text",x=2,y=21.2,label=expression(paste("43.7")),size=4)+
  annotate("text",x=2,y=16.4,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=21.2,label=expression(paste("45.8")),size=4)+
  annotate("text",x=3,y=16.4,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=21.2,label=expression(paste("60.2")),size=4)+
  annotate("text",x=4,y=16.4,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=21.2,label=expression(paste("53.0")),size=4)+
  annotate("text",x=5,y=16.4,label=expression(paste("41")),size=4)+
  annotate("text",x=6,y=21.2,label=expression(paste("63.1")),size=4)+
  annotate("text",x=6,y=16.4,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("bc"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("cd"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("a"))),size=5)

PLAdry_plot

# stat
lm1<-lm(D.PLA~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


# PLLedry
PLLedry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLLe,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Length"["dry"]," (%)")))+
  ylim(-15,20)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=-6,label=expression(paste(italic(bar("x"))," = 1.9")),size=4)+
  annotate("text",x=1,y=-8,label=expression(paste(italic("n")," = 41")),size=4)+
  annotate("text",x=2,y=-6,label=expression(paste("2.0")),size=4)+
  annotate("text",x=2,y=-8,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=-6,label=expression(paste("1.4")),size=4)+
  annotate("text",x=3,y=-8,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=-6,label=expression(paste("2.9")),size=4)+
  annotate("text",x=4,y=-8,label=expression(paste("39")),size=4)+
  annotate("text",x=5,y=-6,label=expression(paste("3.2")),size=4)+
  annotate("text",x=5,y=-8,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=-6,label=expression(paste("3.4")),size=4)+
  annotate("text",x=6,y=-8,label=expression(paste("41")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("bc"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("bc"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("a"))),size=5)

PLLedry_plot
# stat
lm1<-lm(D.PLLe~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# PLWidry (PLW1dry)
PLWdry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLW1,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Width"["dry"]," (%)")))+
  ylim(0,100)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=14,label=expression(paste(italic(bar("x"))," = 49.0")),size=4)+
  annotate("text",x=1,y=8,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=14,label=expression(paste("44.9")),size=4)+
  annotate("text",x=2,y=8,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=14,label=expression(paste("46.8")),size=4)+
  annotate("text",x=3,y=8,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=14,label=expression(paste("57.9")),size=4)+
  annotate("text",x=4,y=8,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=14,label=expression(paste("56.3")),size=4)+
  annotate("text",x=5,y=8,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=14,label=expression(paste("61.6")),size=4)+
  annotate("text",x=6,y=8,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)

PLWdry_plot

# stat
lm1<-lm(D.PLW1~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


# PLV (PLW1dry)
PLV_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLV,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Volume"["dry"]," (%)")))+
  ylim(40,110)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=50,label=expression(paste(italic(bar("x"))," = 71.6")),size=4)+
  annotate("text",x=1,y=45,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=50,label=expression(paste("82.5")),size=4)+
  annotate("text",x=2,y=45,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=50,label=expression(paste("70.5")),size=4)+
  annotate("text",x=3,y=45,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=50,label=expression(paste("82.7")),size=4)+
  annotate("text",x=4,y=45,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=50,label=expression(paste("85.3")),size=4)+
  annotate("text",x=5,y=45,label=expression(paste("41")),size=4)+
  annotate("text",x=6,y=50,label=expression(paste("80.2")),size=4)+
  annotate("text",x=6,y=45,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLV"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLV"],na.rm=T)+8,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLV"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLV"],na.rm=T)+8,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLV"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLV"],na.rm=T)+8,label=expression(paste(bold("b"))),size=5)

PLV_plot


# stat
lm1<-lm(D.PLV~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

##all graphs for leaf structure

# Extract the legend
legend <- get_legend(
  PLV_plot +
    theme(legend.position = "right", text = element_text(size=20)) # Adjust position if needed
)

#legend <- plot(legend) #to check if it plots

#now remove the legend from the PLV plot
PLV_plot <- PLV_plot + theme(legend.position = "none")

Percent_loss_dry<- ggarrange(PLTdry_plot, PLAdry_plot, PLLedry_plot, PLWdry_plot, PLV_plot, legend, ncol =3, nrow = 2)

Percent_loss_dry

ggsave(filename = "../results/Percentloss_dry.jpg", plot = Percent_loss_dry, width = 12, height = 8)

```


## Scatterplots - LMA components

```{r}
# LMA, components ####

# Reorder Species factor
SRCdata$Species <- factor(SRCdata$Species, levels = c("Avsa", "Pegl" , "Trae", "Zema", "Hovu", "Chga"))

# LMA vs LT



LMA_LT<-ggplot(SRCdata,aes(x=T.LT,y=LMA,colour=Metabolism,shape=Species, lty = Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
   ylim(7,45)+
  xlim(0.06,0.31)+
  #geom_hline(yintercept=0,lty=2)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LMA (g m"^-2,")")))+
  xlab(expression(paste("LT (mm)")))+
  annotate("text",x=0.17,y=10,na.rm=T,label=expression(paste(italic("LT: P < 0.001, Sp: P < 0.001, LT x Sp: P = 0.347; R2 = 0.64 "))),size=3)


LMA_LT

# stat
lm1<-lm(LMA~T.LT*Species,data=SRCdata)
anova(lm1)
summary(lm1)

#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)

# LMA vs LD
LMA_LD<-ggplot(SRCdata,aes(x=LD,y=LMA,colour=Metabolism,shape=Species,lty=Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(7,45)+
  xlim(0.04,0.35)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LMA (g m"^-2,")")))+
  xlab(expression(paste("LD (g cm"^-3,")")))+
  annotate("text",x=0.17,y=10,na.rm=T,label=expression(paste(italic("LD: P < 0.001, Sp: P < 0.001, LD x Sp: P < 0.001; R2 = 0.67"))),size=3)

LMA_LD

# stat
lm1<-lm(LMA~LD*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph) #pairwise comparison: significant differences exist between certain species pairs, ex Pegl and Chga when compared to Avsa.For C3 species pairs like Hovu vs. Avsa and Trae vs. Avsa, there are no significant differences.

# LMA vs LDMC

LMA_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=LMA,colour=Metabolism,shape=Species,lty=Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(7,45)+
  xlim(0.04,0.23)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LMA (g m"^-2,")")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=0.14,y=10,na.rm=T,label=expression(paste(italic("LDMC: P < 0.001, Sp: P < 0.001, LDMC x Sp: P < 0.001; R2 = 0.80"))),size=3)


LMA_LDMC

# stat
lm1<-lm(LMA~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)

ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)

# LD vs LDMC

LD_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=LD,colour=Metabolism,shape=Species,lty=Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(0.04,0.35)+
  xlim(0.04,0.23)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  geom_abline(intercept=0,slope=1,colour="darkgrey")+ #slope grey line 1:1
  ylab(expression(paste("LD (g cm"^-3,")")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=0.14,y=0.06,na.rm=T,label=expression(paste(italic("LDMC: P < 0.001, Sp: P < 0.001, LDMC x Sp: P < 0.001; R2 = 0.88"))),size=3)+
  annotate(geom = "text", x= 0.107, y=0.05, label= expression(paste(italic("grey line 1:1"))), size= 3)


LD_LDMC

# stat
lm1<-lm(LD~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)


# LT vs LD
LT_LD<-ggplot(SRCdata,aes(x=LD,y=T.LT,colour=Metabolism,shape=Species,lty=Species))+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(0.06,0.31)+
  xlim(0.04,0.35)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LT (mm)")))+
  xlab(expression(paste("LD (g cm"^-3,")")))+
  annotate("text",x=0.18,y=0.06,na.rm=T,label=expression(paste(italic("LD: P < 0.001, Sp: P < 0.001, LD x Sp: P < 0.001; R2 = 0.72"))),size=3)

LT_LD

# stat
lm1<-lm(T.LT~LD*Species,data=SRCdata)
anova(lm1)
summary(lm1)

ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)

# LT vs LDMC

LT_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=T.LT,colour=Metabolism,shape=Species,lty=Species))+
  ylim(0.06,0.31)+
  xlim(0.04,0.23)+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LT (mm)")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=0.13,y=0.06,na.rm=T,label=expression(paste(italic("LDMC: P = 0.114, Sp: P < 0.001, LDMC x Sp: P = 0.001; R2 = 0.73"))),size=3)

LT_LDMC

# stat
lm1<-lm(T.LT~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)


#all plot 

LMA_component <- ggarrange(LMA_LT, LMA_LD, LMA_LDMC, LD_LDMC, LT_LD, LT_LDMC, common.legend = T, legend = "bottom", ncol = 3, nrow = 2)

LMA_component 

ggsave(filename = "../results/LMA_component.jpg", plot = LMA_component , width = 13.5, height = 9)
```


# Shrinkage

```{r}
# PLV vs PLT dry
PLV_PLT_dry<-ggplot(SRCdata,aes(x=D.PLT,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,99)+
  xlim(10,90)+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=50,y=50,na.rm=T,label=expression(paste(italic("PLTdry: P < 0.001, Sp: P < 0.001, PLTdry x Sp: P < 0.001; R2 = 0.89"))),size=3)+
  xlab(expression(paste("PLT"[dry]," (%)")))+
  ylab(expression(paste("PLV"[dry]," (%)")))
  
PLV_PLT_dry 

# stat
lm1<-lm(D.PLV~D.PLT*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)

y_avsa = 34.63947 + 0.80176 * 50 #correct
y_trae = 34.63947+9.32340 + (0.80176-0.22111)*50
y_hovu = 34.63947-9.73662 + (0.80176+0.02352 )*50
y_pegl = 34.63947+27.45534 + (0.80176-0.43615)*50
y_zema = 34.63947+14.99134 + (0.80176-0.28431)*50
y_chga = 34.63947+27.62275+(0.80176-0.41576 )*50

# PLV vs PLA dry
PLV_PLA_dry<-ggplot(SRCdata,aes(x=D.PLA,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,99)+
  xlim(20,80)+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=50,y=50,na.rm=T,label=expression(paste(italic("PLAdry: P < 0.001, Sp: P < 0.001, PLAdry x Sp: P < 0.001; R2 = 0.78"))),size=3)+
  xlab(expression(paste("PLA"[dry]," (%)")))+
  ylab(expression(paste("PLV"[dry]," (%)")))

y_avsa = 20.54113 + 1.04091 * 50 #correct
y_trae = 20.54113+19.37115 + (1.04091-0.37224)*50
y_hovu = 20.54113+39.62089 + (1.04091-0.52901 )*50
y_pegl = 20.54113+39.94866 + (1.04091-0.67127)*50
y_zema = 20.54113+43.59089 + (1.04091-0.64025)*50
y_chga = 20.54113+23.08392+(1.04091-0.46169)*50

PLV_PLA_dry

# stat
lm1<-lm(D.PLV~D.PLA*Species,data=SRCdata)
anova(lm1)
summary(lm1)
#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)

#PLV_LD
PLV_LD<-ggplot(SRCdata,aes(x=LD,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,98)+
  xlim(0.04,0.35)+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=0.2,y=50,na.rm=T,label=expression(paste(italic("LD: P < 0.001, Sp: P < 0.001, LD x Sp: P < 0.001; R2 = 0.68"))),size=3)+
  ylab(expression(paste("PLV"[dry]," (%)")))+
  xlab(expression(paste("LD (g cm"^-3,")")))

PLV_LD

# stat
lm1<-lm(D.PLV~LD*Species,data=SRCdata)
anova(lm1)
summary(lm1)
#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)


#PLV  LDMC

PLV_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,98)+
  xlim(0.04,0.23)+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=0.13,y=50,na.rm=T,label=expression(paste(italic("LDMC: P < 0.001, Sp: P < 0.001, LDMC x Sp: P < 0.001; R2 = 0.76"))),size=3)+
  ylab(expression(paste("PLV"[dry]," (%)")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))

PLV_LDMC

# stat
lm1<-lm(D.PLV~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)
#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)

#all plot 

Shrinkage_component <- ggarrange(PLV_PLT_dry, PLV_PLA_dry ,PLV_LD, PLV_LDMC, common.legend = T, legend = "bottom", ncol = 2, nrow = 2)

Shrinkage_component 

ggsave(filename = "../results/Shrinkage_component.jpg", plot = Shrinkage_component , width = 10, height = 7)


```

# SRC, dehydration/rehydration analysis 

F for after dehydration or fresh -- STAGE 2
R for Rehydration -- STAGE 3

```{r}
# all species, facet ####
# FvFm

SRCdata$F.FvFm <- as.numeric(SRCdata$F.FvFm)
SRCdata$R.FvFm <- as.numeric(SRCdata$R.FvFm)
SRCdata <- SRCdata %>%
  mutate(Name = case_when(
    Species =="Avsa" ~ "A. sativa",
    Species =="Hovu"~ "H. vulgare",
    Species =="Trae"~ "T. aestivum",
    Species =="Zema"~ "Z. mays",
    Species =="Pegl"~ "P. glaucum",
    Species == "Chga"~"C. gayan"))

SRCdata$Name<- as.factor(SRCdata$Name)
SRCdata$Metabolism <- as.factor(SRCdata$Metabolism)


# "Avsa"
data_subset_avsa <- SRCdata[SRCdata$Species == "Avsa", ]

Avsa <- ggplot(data=data_subset_avsa, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("A. sativa")

# "Hovu"
data_subset_Hovu <- SRCdata[SRCdata$Species == "Hovu", ]

Hovu <- ggplot(data=data_subset_Hovu, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("H. vulgare")


# "Trae"
data_subset_Trae <- SRCdata[SRCdata$Species == "Trae", ]

Trae <- ggplot(data=data_subset_Trae, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("T. aestivum")

# "Pegl"
data_subset_Pegl <- SRCdata[SRCdata$Species == "Pegl", ]

Pegl <- ggplot(data=data_subset_Pegl, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("P. glaucum")

# "Chla"
data_subset_Chga <- SRCdata[SRCdata$Species == "Chga", ]

Chga <- ggplot(data=data_subset_Chga, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("C. gayan")


# "Zema"
data_subset_Zema <- SRCdata[SRCdata$Species == "Zema", ]

Zema <- ggplot(data=data_subset_Zema, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("Z. mays")

FVFM_plot <- ggarrange(Avsa, Trae, Hovu, Pegl, Chga, Zema, ncol = 3, nrow = 2)

ggsave(filename = "../results/FVFM_dehydration_rehydration.jpg", plot = FVFM_plot , width = 10, height = 7)

```

#RWC and water potential

I really don't have the same graph as Miquel... why?

```{r}
# water potential - 'mean'
SRCdata$WPleaf2 <- as.numeric(SRCdata$WPleaf2)

g1<-ggplot(data=SRCdata,aes(x=F.RWC,y=WPleaf2))+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_point(size=3,shape=21,fill="black",alpha=0.5)+
  geom_smooth(aes(x=F.RWC,y=WPleaf2),color="black",fill="grey")+
  #scale_y_continuous(limits=c(-0.25,0.8),breaks=c(0,0.25,0.5,0.75))+
  scale_x_continuous(limits=c(0,100))+
  #xlim(0,1)+
  facet_wrap(~Species,ncol=3)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13,face="italic"))+
  ylab(expression(paste(Psi["leaf"]," (MPa)")))+
  xlab(expression(paste("RWC (%)")))

```

#RWC PLRC
```{r}
# data per species, FvFm, PLRC ####
SRCdata$F.RWC <- as.numeric(SRCdata$F.RWC)
SRCdata$F.FvFm <- as.numeric(SRCdata$F.FvFm)
SRCdata$T.FvFm <- as.numeric(SRCdata$T.FvFm)
SRCdata$R.FvFm <- as.numeric(SRCdata$R.FvFm)
SRCdata$PLRC

# Avsa ----

SRCdata_avsa <- SRCdata %>% filter(Species== "Avsa")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_avsa$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_avsa)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_avsa, start = start)
summary(model)

plot(SRCdata_avsa$F.RWC, SRCdata_avsa$PLRC)
lines(SRCdata_avsa$F.RWC, predict(model, list(x = SRCdata_avsa$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.avsa <- seq(min(SRCdata_avsa$F.RWC,na.rm =T ), max(SRCdata_avsa$F.RWC, na.rm = T), length.out = length(SRCdata_avsa$F.RWC))
y_model.avsa <-  90.687433   * exp(-0.036148   * x_seq.avsa ) -5.710108

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
avsa_10= (1/-0.036148) * (log(10+5.710108) - log(90.687433))
avsa_50= (1/-0.036148) * (log(50+5.710108) - log(90.687433))

Avsa_PLRC<-ggplot(SRCdata_avsa,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_avsa,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.avsa, y = y_model.avsa), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=avsa_10,color="blue",lty=3)+
  geom_vline(xintercept=avsa_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("A. sativa")+
  geom_rect(data=data.frame(xmin=16,xmax=75,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),alpha=0.05,fill="royalblue",inherit.aes=F) #shaded blue area denotes embolism events according to OV method
Avsa_PLRC




# Hovu -----
SRCdata_hovu <- SRCdata %>% filter(Species== "Hovu")
# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_hovu$PLRC, na.rm = T) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_hovu)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_hovu, start = start)
summary(model)

plot(SRCdata_hovu$F.RWC, SRCdata_hovu$PLRC)
lines(SRCdata_hovu$F.RWC, predict(model, list(x = SRCdata_hovu$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.hovu <- seq(min(SRCdata_hovu$F.RWC,na.rm =T ), max(SRCdata_hovu$F.RWC, na.rm = T), length.out = length(SRCdata_avsa$F.RWC))
y_model.hovu <-  102.21313   * exp(-0.03123    * x_seq.hovu ) -6.81649

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
hovu_10= (1/-0.03123) * (log(10+6.81649) - log(102.21313))
hovu_50= (1/-0.03123) * (log(50+6.81649) - log(102.21313))

hovu_PLRC<-ggplot(SRCdata_hovu,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_hovu,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.hovu, y = y_model.hovu), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=hovu_10,color="blue",lty=3)+
  geom_vline(xintercept=hovu_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("H. vulgare")+
  geom_rect(data=data.frame(xmin=22,xmax=74,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=23,xmax=60,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=19,xmax=74,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)
hovu_PLRC


# Trae -----
SRCdata_trae <- SRCdata %>% filter(Species== "Trae")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_trae$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_trae)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_trae, start = start)
summary(model)

plot(SRCdata_trae$F.RWC, SRCdata_trae$PLRC)
lines(SRCdata_trae$F.RWC, predict(model, list(x = SRCdata_trae$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.trae <- seq(min(SRCdata_trae$F.RWC,na.rm =T ), max(SRCdata_trae$F.RWC, na.rm = T), length.out = length(SRCdata_trae$F.RWC))
y_model.trae <-  73.578960   * exp(-0.012623   * x_seq.trae ) -21.445047

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
trae_10= (1/-0.012623) * (log(10+21.445047) - log(73.578960))
trae_50= (1/-0.012623) * (log(50+21.445047) - log(73.578960))

trae_PLRC<-ggplot(SRCdata_trae,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_trae,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.trae, y = y_model.trae), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=trae_10,color="blue",lty=3)+
  geom_vline(xintercept=trae_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("T. aestivum")+
  geom_rect(data=data.frame(xmin=11.5,xmax=61.5,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=23,xmax=70,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=44,xmax=72,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
trae_PLRC



# Pegl ----
SRCdata_Pegl <- SRCdata %>% filter(Species== "Pegl")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Pegl$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_Pegl)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Pegl, start = start)
summary(model)

plot(SRCdata_Pegl$F.RWC, SRCdata_Pegl$PLRC)
lines(SRCdata_Pegl$F.RWC, predict(model, list(x = SRCdata_Pegl$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Pegl <- seq(min(SRCdata_Pegl$F.RWC,na.rm =T ), max(SRCdata_Pegl$F.RWC, na.rm = T), length.out = length(SRCdata_Pegl$F.RWC))
y_model.Pegl <-  88.052445   * exp(-0.024293   * x_seq.Pegl )-10.882535

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Pegl_10= (1/-0.024293) * (log(10+10.882535) - log(88.052445))
Pegl_50= (1/-0.024293) * (log(50+10.882535) - log(88.052445))

Pegl_PLRC<-ggplot(SRCdata_Pegl,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_Pegl,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  geom_line(aes(x = x_seq.Pegl, y = y_model.Pegl), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=Pegl_10,color="blue",lty=3)+
  geom_vline(xintercept=Pegl_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("P. glaucum")+
  geom_rect(data=data.frame(xmin=7,xmax=9,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=20,xmax=30,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Pegl_PLRC


# Zema -----
SRCdata_Zema <- SRCdata %>% filter(Species== "Zema")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Zema$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_Zema)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Zema, start = start)
summary(model)

plot(SRCdata_Zema$F.RWC, SRCdata_Zema$PLRC)
lines(SRCdata_Zema$F.RWC, predict(model, list(x = SRCdata_Zema$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Zema <- seq(min(SRCdata_Zema$F.RWC,na.rm =T ), max(SRCdata_Zema$F.RWC, na.rm = T), length.out = length(SRCdata_Zema$F.RWC))
y_model.Zema <-  125.602294   * exp(-0.009158   * x_seq.Zema )-53.577050

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Zema_10= (1/-0.009158) * (log(10+53.577050) - log(125.602294))
Zema_50= (1/-0.009158) * (log(50+53.577050) - log(125.602294))

Zema_PLRC<-ggplot(SRCdata_Zema,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_Zema,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  geom_line(aes(x = x_seq.Zema, y = y_model.Zema), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=Zema_10,color="blue",lty=3)+
  geom_vline(xintercept=Zema_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("Z. mays")+
  geom_rect(data=data.frame(xmin=4,xmax=5,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=11,xmax=35,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Zema_PLRC

# Chga----
SRCdata_Chga <- SRCdata %>% filter(Species== "Chga")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Chga$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_Chga)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Chga, start = start)
summary(model)

plot(SRCdata_Chga$F.RWC, SRCdata_Chga$PLRC)
lines(SRCdata_Chga$F.RWC, predict(model, list(x = SRCdata_Chga$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Chga <- seq(min(SRCdata_Chga$F.RWC,na.rm =T ), max(SRCdata_Chga$F.RWC, na.rm = T), length.out = length(SRCdata_Chga$F.RWC))
y_model.Chga <-  125.602294   * exp(-0.009158   * x_seq.Chga )-53.577050

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Chga_10= (1/-0.009158) * (log(10+53.577050) - log(125.602294))
Chga_50= (1/-0.009158) * (log(50+53.577050) - log(125.602294))

Chga_PLRC<-ggplot(SRCdata_Chga,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_Chga,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  geom_line(aes(x = x_seq.Chga, y = y_model.Chga), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=Chga_10,color="blue",lty=3)+
  geom_vline(xintercept=Chga_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("C. gayan")+
  geom_rect(data=data.frame(xmin=9,xmax=10,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=9,xmax=10,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=7,xmax=40,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Chga_PLRC

### all plots ----
PLRC_RWC_plot <- ggarrange(Avsa_PLRC, hovu_PLRC, trae_PLRC, Pegl_PLRC, Zema_PLRC, Chga_PLRC, ncol =3, nrow = 2)

PLRC_RWC_plot 

ggsave(filename = "../results/PLRC_RWC_plot .jpg", plot = PLRC_RWC_plot, width = 12, height = 8)

### means----------
rating <- 1:4

animal <- c('koala', 'hedgehog', 'sloth', 'panda') 
country <- c('Australia', 'Italy', 'Peru', 'China')
avg_sleep_hours <- c(21, 18, 17, 10)
super_sleepers <- data.frame(rating, animal, country, avg_sleep_hours)
data <- as.data.frame(x = Chga_10
Chga_50)

mean_RWC<-ddply(SRCdata,c("Species","Metabolism"),summarise,
                m.LMA=mean(LMA,na.rm=TRUE),n.LMA=sum(!is.na(LMA)),se.LMA=sd(LMA,na.rm=T)/sqrt(n.LMA),
```

#data per species, Shrinkage ####
```{r}


# 
# Avsa
g1<-ggplot()+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_vline(xintercept=89.5,color="black",lty=2)+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_hline(yintercept=10,color="grey",lty=2)+
  geom_hline(yintercept=25,color="darkgrey",lty=2)+
  geom_hline(yintercept=50,color="black",lty=2)+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLV),size=2,shape=21,alpha=0.5,fill="forestgreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLV),color="forestgreen",fill="forestgreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLT),size=2,shape=21,alpha=0.5,fill="chartreuse")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLT),color="chartreuse3",fill="chartreuse")+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLA),size=2,shape=21,alpha=0.5,fill="palegreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLA),color="chartreuse2",fill="palegreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLW1),size=2,shape=21,alpha=0.5,fill="white",colour="chartreuse2")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLW1),color="chartreuse2",fill="palegreen",lty=2)+
  ylim(-10,100)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=10),
        axis.text.y=element_text(size=9),
        axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=9))+
  ylab(expression(paste("Shrinkage; PLV,PLT,PLA,PLWi (%)")))+
  xlab(expression(paste("RWC (%)")))+
  annotate("text",x=75,y=97,label=expression(paste(italic("Avsa"))))
# Hovu
g1<-ggplot()+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_vline(xintercept=90.7,color="black",lty=2)+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_hline(yintercept=10,color="grey",lty=2)+
  geom_hline(yintercept=25,color="darkgrey",lty=2)+
  geom_hline(yintercept=50,color="black",lty=2)+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLV),size=2,shape=21,alpha=0.5,fill="forestgreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLV),color="forestgreen",fill="forestgreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLT),size=2,shape=21,alpha=0.5,fill="chartreuse")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLT),color="chartreuse3",fill="chartreuse")+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLA),size=2,shape=21,alpha=0.5,fill="palegreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLA),color="chartreuse2",fill="palegreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLW1),size=2,shape=21,alpha=0.5,fill="white",colour="chartreuse2")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLW1),color="chartreuse2",fill="palegreen",lty=2)+
  ylim(-10,100)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=10),
        axis.text.y=element_text(size=9),
        axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=9))+
  ylab(expression(paste("Shrinkage; PLV,PLT,PLA,PLWi (%)")))+
  xlab(expression(paste("RWC (%)")))+
  annotate("text",x=75,y=97,label=expression(paste(italic("Hovu"))))
# Trae
g1<-ggplot()+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_vline(xintercept=90.0,color="black",lty=2)+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_hline(yintercept=10,color="grey",lty=2)+
  geom_hline(yintercept=25,color="darkgrey",lty=2)+
  geom_hline(yintercept=50,color="black",lty=2)+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLV),size=2,shape=21,alpha=0.5,fill="forestgreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLV),color="forestgreen",fill="forestgreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLT),size=2,shape=21,alpha=0.5,fill="chartreuse")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLT),color="chartreuse3",fill="chartreuse")+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLA),size=2,shape=21,alpha=0.5,fill="palegreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLA),color="chartreuse2",fill="palegreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLW1),size=2,shape=21,alpha=0.5,fill="white",colour="chartreuse2")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLW1),color="chartreuse2",fill="palegreen",lty=2)+
  ylim(-10,100)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=10),
        axis.text.y=element_text(size=9),
        axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=9))+
  ylab(expression(paste("Shrinkage; PLV,PLT,PLA,PLWi (%)")))+
  xlab(expression(paste("RWC (%)")))+
  annotate("text",x=75,y=97,label=expression(paste(italic("Trae"))))
# Pegl
g1<-ggplot()+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_vline(xintercept=91.2,color="black",lty=2)+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_hline(yintercept=10,color="grey",lty=2)+
  geom_hline(yintercept=25,color="darkgrey",lty=2)+
  geom_hline(yintercept=50,color="black",lty=2)+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLV),size=2,shape=21,alpha=0.5,fill="forestgreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLV),color="forestgreen",fill="forestgreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLT),size=2,shape=21,alpha=0.5,fill="chartreuse")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLT),color="chartreuse3",fill="chartreuse")+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLA),size=2,shape=21,alpha=0.5,fill="palegreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLA),color="chartreuse2",fill="palegreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLW1),size=2,shape=21,alpha=0.5,fill="white",colour="chartreuse2")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLW1),color="chartreuse2",fill="palegreen",lty=2)+
  ylim(-10,100)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=10),
        axis.text.y=element_text(size=9),
        axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=9))+
  ylab(expression(paste("Shrinkage; PLV,PLT,PLA,PLWi (%)")))+
  xlab(expression(paste("RWC (%)")))+
  annotate("text",x=75,y=97,label=expression(paste(italic("Pegl"))))
# Zema
g1<-ggplot()+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_vline(xintercept=91.8,color="black",lty=2)+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_hline(yintercept=10,color="grey",lty=2)+
  geom_hline(yintercept=25,color="darkgrey",lty=2)+
  geom_hline(yintercept=50,color="black",lty=2)+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLV),size=2,shape=21,alpha=0.5,fill="forestgreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLV),color="forestgreen",fill="forestgreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLT),size=2,shape=21,alpha=0.5,fill="chartreuse")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLT),color="chartreuse3",fill="chartreuse")+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLA),size=2,shape=21,alpha=0.5,fill="palegreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLA),color="chartreuse2",fill="palegreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLW1),size=2,shape=21,alpha=0.5,fill="white",colour="chartreuse2")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLW1),color="chartreuse2",fill="palegreen",lty=2)+
  ylim(-10,100)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=10),
        axis.text.y=element_text(size=9),
        axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=9))+
  ylab(expression(paste("Shrinkage; PLV,PLT,PLA,PLWi (%)")))+
  xlab(expression(paste("RWC (%)")))+
  annotate("text",x=75,y=97,label=expression(paste(italic("Zema"))))
# Chga
g1<-ggplot()+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_vline(xintercept=93.1,color="black",lty=2)+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_hline(yintercept=10,color="grey",lty=2)+
  geom_hline(yintercept=25,color="darkgrey",lty=2)+
  geom_hline(yintercept=50,color="black",lty=2)+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLV),size=2,shape=21,alpha=0.5,fill="forestgreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLV),color="forestgreen",fill="forestgreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLT),size=2,shape=21,alpha=0.5,fill="chartreuse")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLT),color="chartreuse3",fill="chartreuse")+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLA),size=2,shape=21,alpha=0.5,fill="palegreen")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLA),color="chartreuse2",fill="palegreen")+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLW1),size=2,shape=21,alpha=0.5,fill="white",colour="chartreuse2")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLW1),color="chartreuse2",fill="palegreen",lty=2)+
  ylim(-10,100)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=10),
        axis.text.y=element_text(size=9),
        axis.title.x=element_text(size=10),
        axis.text.x=element_text(size=9))+
  ylab(expression(paste("Shrinkage; PLV,PLT,PLA,PLWi (%)")))+
  xlab(expression(paste("RWC (%)")))+
  annotate("text",x=75,y=97,label=expression(paste(italic("Chga"))))

```
