---
title: "Script Marion Analyses"
author: "Marion Boisseaux"
date: "2025-01-14"
output: html_document
---

C3C4 Grasses CALSTATE LA 

#libraries 

```{r}
library(ggplot2)
library(agricolae)
library(plyr)
library(multcomp)
library(corrplot)
library(factoextra)
library(readxl)
library(dplyr)
library(ggpubr)
library(cowplot)
```

#Leaf dehydration and recovery assay

##data 
SRC, data loading, variable calculation, outliers, means 
```{r}
SRCdata <- read_xlsx(path = "../data/C3C4 Grasses - OV monitoring, SRC.xlsx", sheet = "C3C4G SRC") 

```

##variable calculations
```{r}
SRCdata$Metabolism<-factor(SRCdata$Metabolism)
SRCdata$Species<-factor(SRCdata$Species,levels=c("Avsa","Hovu","Trae","Pegl","Zema","Chga"))

# variable calculation
#T for initial, fully hydrated or turgid -- STAGE 1
#F for after dehydration or fresh -- STAGE 2
#R for Rehydration -- STAGE 3
#D for dry -- STAGE 4

#leaf thickness average
SRCdata$T.LT<-rowMeans(SRCdata[c("T.LT1","T.LT2","T.LT3","T.LT4","T.LT5","T.LT6")],na.rm=T) #stage 1
SRCdata$F.LT2 <- as.numeric(SRCdata$F.LT2)
SRCdata$F.LT<-rowMeans(SRCdata[c("F.LT1","F.LT2","F.LT3","F.LT4","F.LT5","F.LT6")],na.rm=T) #stage 2
SRCdata$D.LT2 <- as.numeric(SRCdata$D.LT2)
SRCdata$D.LT<-rowMeans(SRCdata[c("D.LT1","D.LT2","D.LT3","D.LT4","D.LT5","D.LT6")],na.rm=T) #stage 4

#leaf width average
SRCdata$F.LW1 <- as.numeric(SRCdata$F.LW1)
SRCdata$F.LW2 <- as.numeric(SRCdata$F.LW2)
SRCdata$F.LW3 <- as.numeric(SRCdata$F.LW3)
SRCdata$F.LW4 <- as.numeric(SRCdata$F.LW4)
SRCdata$F.LW5 <- as.numeric(SRCdata$F.LW5)

SRCdata$T.LW1<-rowMeans(SRCdata[c("T.LW1","T.LW2","T.LW3")],na.rm=T) #stage 1 - middle
SRCdata$F.LW1<-rowMeans(SRCdata[c("F.LW1","F.LW2","F.LW3")],na.rm=T) #stage 2
SRCdata$T.LW2<-rowMeans(SRCdata[c("T.LW1","T.LW4","T.LW5")],na.rm=T) #stage 1 - base
SRCdata$F.LW2<-rowMeans(SRCdata[c("F.LW1","F.LW4","F.LW5")],na.rm=T) #stage 2

SRCdata$D.LW1 <- as.numeric(SRCdata$D.LW1)
SRCdata$D.LW2 <- as.numeric(SRCdata$D.LW2)
SRCdata$D.LW3 <- as.numeric(SRCdata$D.LW3)
SRCdata$D.LW4 <- as.numeric(SRCdata$D.LW4)
SRCdata$D.LW5 <- as.numeric(SRCdata$D.LW5)

SRCdata$D.LW<-rowMeans(SRCdata[c("D.LW1","D.LW2","D.LW3","D.LW4","D.LW5")],na.rm=T) #stage 4

#Leaf volume 
SRCdata$F.LA <- as.numeric(SRCdata$F.LA)
SRCdata$D.LA <- as.numeric(SRCdata$D.LA)

SRCdata$T.LV<-SRCdata$T.LA*SRCdata$T.LT/10 #stage 1
SRCdata$F.LV<-SRCdata$F.LA*SRCdata$F.LT/10 #stage 2
SRCdata$D.LV<-SRCdata$D.LA*SRCdata$D.LT/10  #stage 4

```

#PLX : Leaf percentage loss of X variable
```{r}

#Leaf percentage loss during dehydration: thickness
SRCdata$F.PLT<-100-SRCdata$F.LT/SRCdata$T.LT*100 #stage 2 leaf thickness compared to stage 1 leaf thickness
SRCdata$D.PLT<-100-SRCdata$D.LT/SRCdata$T.LT*100 #stage 4 dry leaf thickness compared to stage 4 

#Leaf percentage loss during dehydration: leaf area
SRCdata$F.PLA<-100-SRCdata$F.LA/SRCdata$T.LA*100
SRCdata$D.PLA<-100-SRCdata$D.LA/SRCdata$T.LA*100

#Leaf percentage loss during dehydration: leaf width
SRCdata$F.PLW1<-100-SRCdata$F.LW1/SRCdata$T.LW1*100
SRCdata$D.PLW1<-100-SRCdata$D.LW/SRCdata$T.LW1*100

#Leaf percentage loss during dehydration: leaf length
SRCdata$F.LLe <- as.numeric(SRCdata$F.LLe)
SRCdata$T.LLe <- as.numeric(SRCdata$T.LLe)
SRCdata$D.LLe <- as.numeric(SRCdata$D.LLe)
SRCdata$F.PLLe<-100-SRCdata$F.LLe/SRCdata$T.LLe*100
SRCdata$D.PLLe<-100-SRCdata$D.LLe/SRCdata$T.LLe*100

##Leaf percentage loss during dehydration: leaf volume
SRCdata$F.PLV<-100-SRCdata$F.LV/SRCdata$T.LV*100
SRCdata$D.PLV<-100-SRCdata$D.LV/SRCdata$T.LV*100

```

#RWC calculations & other variables
```{r}
#RWC calculations
SRCdata$T.SWC<-(SRCdata$TW-SRCdata$DW)/SRCdata$DW
SRCdata$F.SWC<-(SRCdata$FW-SRCdata$DW)/SRCdata$DW
SRCdata$R.SWC<-(SRCdata$RW-SRCdata$DW)/SRCdata$DW
SRCdata$F.RWC<-(SRCdata$FW-SRCdata$DW)/(SRCdata$TW-SRCdata$DW)*100

#??
SRCdata$F.1_LWi.LWhy<-1-SRCdata$FW/SRCdata$TW #???

#LMA, leaf density, LDMC, 
SRCdata$LMA<-SRCdata$DW/1000/(SRCdata$T.LA/10000)
SRCdata$LD<-SRCdata$DW/1000/SRCdata$T.LV
SRCdata$LDMC<-SRCdata$DW/SRCdata$TW

#Rehydration capacity PLRC = 100- LW_rehy / LW_full saturation *100
#what the leaf recovers compared to its full turgid capacity
SRCdata$PLRC<-100-SRCdata$R.SWC/SRCdata$T.SWC*100

#formula for the percentage loss of chlorophyll fluorescence (PLCF, in %), as an index of loss of fluorescence  capacity after dehydration

# variable calculation
#T for initial, fully hydrated or turgid -- STAGE 1
#F for after dehydration or fresh -- STAGE 2
#R for Rehydration -- STAGE 3
#D for dry -- STAGE 4

SRCdata$PLCF = 100* (1- (SRCdata$F.FvFm/SRCdata$T.FvFm))

```

# SRC, outliers

```{r}
# PLRC of -20% 
#SRCdata$Species[!SRCdata$PLRC>-20] (Chga and Hovu)
SRCdata$PLRC[!SRCdata$PLRC>-20]<-NA #why input NA for the two values: -23.9 and -21.5?

```

#Species 
## AVSA

Question; what's the justification to put NAs for ex. Leaf 22 column 5 though 84 ??? 
```{r}
# Avsa
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==17,5:84]<-NA
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==20,5:84]<-NA
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==21,5:84]<-NA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==22,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==24,5:84]<-NA
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==25,5:84]<-NA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==26,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==29,5:84]<-NA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==30,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==31,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==32,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==43,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==44,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==45,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==46,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==47,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==49,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==51,5:84]<-NA # too small leaf (!)
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==52,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==53,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==54,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==55,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==56,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==57,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==59,5:84]<-NA # PLA
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==17,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==20,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==21,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==24,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==25,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==24,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==27,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==28,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==65,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==66,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Avsa" & SRCdata$Leaf==48,70]<-NA # only D.PLA - to check photos!
```


## Chga
```{r}
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==1,5:84]<-NA # PLT - to check
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==6,5:84]<-NA # PLA - to check photos!
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==9,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==21,5:84]<-NA # PLT - to check
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==22,5:84]<-NA # LMA vs LDMC
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==24,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==25,5:84]<-NA # LMA vs LDMC
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==30,5:84]<-NA # PLT - to check
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==31,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==32,5:84]<-NA # PLRC
SRCdata[SRCdata$Species=="Chga" & SRCdata$Leaf==48,5:84]<-NA # FvFm
```


## Hovu
```{r}
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==3,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==4,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==5,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==6,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==7,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==8,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==15,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==17,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==19,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==49,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==50,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==56,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==55,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Hovu" & SRCdata$Leaf==14,c(69,75)]<-NA # only PLA, PLV - to check photos!
```


## Pegl 
```{r}
SRCdata[SRCdata$Species=="Pegl" & SRCdata$Leaf==35,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Pegl" & SRCdata$Leaf==38,74]<-NA # only D.PLLe - to check photos!
SRCdata[SRCdata$Species=="Pegl" & SRCdata$Leaf==42,74]<-NA # only D.PLLe - to check photos!
```


## Trae
```{r}
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==8,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==9,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==10,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==18,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==20,5:84]<-NA # FvFm
#SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==23,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==28,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==29,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==30,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==31,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==32,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==45,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==46,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==47,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==49,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==50,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==52,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==53,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Trae" & SRCdata$Leaf==42,44]<-NA # only R FvFm - to check!
```


## Zema
```{r}
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==8,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==10,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==15,5:84]<-NA # LDMC vs LD
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==20,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==23,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==34,5:84]<-NA # FvFm
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==24,84]<-NA # only PLRC
SRCdata[SRCdata$Species=="Zema" & SRCdata$Leaf==6,c(70,76)]<-NA # only DPLA, DPLV - to check photos!
```


## means 
```{r}
m.SRCdata<-ddply(SRCdata,c("Species","Metabolism"),summarise,
                m.LMA=mean(LMA,na.rm=TRUE),n.LMA=sum(!is.na(LMA)),se.LMA=sd(LMA,na.rm=T)/sqrt(n.LMA),
                m.T.LT=mean(T.LT,na.rm=TRUE),n.T.LT=sum(!is.na(T.LT)),se.T.LT=sd(T.LT,na.rm=T)/sqrt(n.T.LT),
                m.LD=mean(LD,na.rm=TRUE),n.LD=sum(!is.na(LD)),se.LD=sd(LD,na.rm=T)/sqrt(n.LD),
                m.LDMC=mean(LDMC,na.rm=TRUE),n.LDMC=sum(!is.na(LDMC)),se.LDMC=sd(LDMC,na.rm=T)/sqrt(n.LDMC),
                m.D.PLT=mean(D.PLT,na.rm=TRUE),n.D.PLT=sum(!is.na(D.PLT)),se.D.PLT=sd(D.PLT,na.rm=T)/sqrt(n.D.PLT),
                m.D.PLA=mean(D.PLA,na.rm=TRUE),n.D.PLA=sum(!is.na(D.PLA)),se.D.PLA=sd(D.PLA,na.rm=T)/sqrt(n.D.PLA),
                m.D.PLV=mean(D.PLV,na.rm=TRUE),n.D.PLV=sum(!is.na(D.PLV)),se.D.PLV=sd(D.PLV,na.rm=T)/sqrt(n.D.PLV),
                m.D.PLLe=mean(D.PLLe,na.rm=TRUE),n.D.PLLe=sum(!is.na(D.PLLe)),se.D.PLLe=sd(D.PLLe,na.rm=T)/sqrt(n.D.PLLe),
                m.D.PLW1=mean(D.PLW1,na.rm=TRUE),n.D.PLW1=sum(!is.na(D.PLW1)),se.D.PLW1=sd(D.PLW1,na.rm=T)/sqrt(n.D.PLW1))
```

#Analysis

##leaf structure
```{r}
## SRC, boxplots, stat analysis ####

# LMA
plot_LMA<-ggplot(SRCdata,aes(x=Species,y=LMA,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("LMA (g m"^-2,")")))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,50)+
  #geom_hline(yintercept=0,lty=2)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  #ylab(expression(paste("LMA (g m"^-2,")")))+
  annotate("text",x=1,y=7,label=expression(paste(italic(bar("x"))," = 31.1")),size=4)+
  annotate("text",x=1,y=4,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=7,label=expression(paste("21.2")),size=4)+
  annotate("text",x=2,y=4,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=7,label=expression(paste("27.4")),size=4)+
  annotate("text",x=3,y=4,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=7,label=expression(paste("24.7")),size=4)+
  annotate("text",x=4,y=4,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=7,label=expression(paste("20.6")),size=4)+
  annotate("text",x=5,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=7,label=expression(paste("27.5")),size=4)+
  annotate("text",x=6,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","LMA"],na.rm=T)+4,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","LMA"],na.rm=T)+4,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","LMA"],na.rm=T)+4,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","LMA"],na.rm=T)+4,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","LMA"],na.rm=T)+4,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","LMA"],na.rm=T)+4,label=expression(paste(bold("b"))),size=5)
plot_LMA

# stat
lm1<-lm(LMA~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# LT
plot_LT<-ggplot(SRCdata,aes(x=Species,y=T.LT,fill=Metabolism))+
  theme_minimal()+
  geom_boxplot(lwd=0.2,fatten=5)+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,0.4)+
  #geom_hline(yintercept=0,lty=2)+
  ggtitle("LT (mm)")+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=0.056,label=expression(paste(italic(bar("x"))," = 0.22")),size=4)+
  annotate("text",x=1,y=0.032,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=0.056,label=expression(paste("0.19")),size=4)+
  annotate("text",x=2,y=0.032,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=0.056,label=expression(paste("0.17")),size=4)+
  annotate("text",x=3,y=0.032,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=0.056,label=expression(paste("0.13")),size=4)+
  annotate("text",x=4,y=0.032,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=0.056,label=expression(paste("0.16")),size=4)+
  annotate("text",x=5,y=0.032,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=0.056,label=expression(paste("0.12")),size=4)+
  annotate("text",x=6,y=0.032,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","T.LT"],na.rm=T)+0.032,label=expression(paste(bold("e"))),size=5)
plot_LT

# stat
lm1<-lm(T.LT~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# LD
plot_LD<-ggplot(SRCdata,aes(x=Species,y=LD,fill=Metabolism))+
  theme_minimal()+
  geom_boxplot(lwd=0.2,fatten=5)+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,0.4)+
  #geom_hline(yintercept=0,lty=2)+
  ggtitle(expression(paste("LD (g cm"^-3,")")))+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=0.040,label=expression(paste(italic(bar("x"))," = 0.14")),size=4)+
  annotate("text",x=1,y=0.016,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=0.040,label=expression(paste("0.11")),size=4)+
  annotate("text",x=2,y=0.016,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=0.040,label=expression(paste("0.17")),size=4)+
  annotate("text",x=3,y=0.016,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=0.040,label=expression(paste("0.19")),size=4)+
  annotate("text",x=4,y=0.016,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=0.040,label=expression(paste("0.13")),size=4)+
  annotate("text",x=5,y=0.016,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=0.040,label=expression(paste("0.24")),size=4)+
  annotate("text",x=6,y=0.016,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","LD"],na.rm=T)+0.032,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","LD"],na.rm=T)+0.032,label=expression(paste(bold("e"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","LD"],na.rm=T)+0.032,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","LD"],na.rm=T)+0.032,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","LD"],na.rm=T)+0.032,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","LD"],na.rm=T)+0.032,label=expression(paste(bold("a"))),size=5)
plot_LD

# stat
lm1<-lm(LD~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# LDMC
plot_LDMC<-ggplot(SRCdata,aes(x=Species,y=LDMC,fill=Metabolism))+
  theme_minimal()+
  geom_boxplot(lwd=0.2,fatten=5)+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
  #geom_point(data=GExdata.0[GExdata.0$Dataset=="Dehydration",],aes(x=Species,y=LMA),size=4,shape=21,fill="yellow")+
  ylim(0,0.3)+
  #geom_hline(yintercept=0,lty=2)+
  ggtitle(expression(paste("LDMC (g g"^-1,")")))+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  #ylab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=1,y=0.024,label=expression(paste(italic(bar("x"))," = 0.13")),size=4)+
  annotate("text",x=1,y=0,label=expression(paste(italic("n")," = 44")),size=4)+
  annotate("text",x=2,y=0.024,label=expression(paste("0.11")),size=4)+
  annotate("text",x=2,y=0,label=expression(paste("47")),size=4)+
  annotate("text",x=3,y=0.024,label=expression(paste("0.16")),size=4)+
  annotate("text",x=3,y=0,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=0.024,label=expression(paste("0.11")),size=4)+
  annotate("text",x=4,y=0,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=0.024,label=expression(paste("0.10")),size=4)+
  annotate("text",x=5,y=0,label=expression(paste("41")),size=4)+
  annotate("text",x=6,y=0.024,label=expression(paste("0.16")),size=4)+
  annotate("text",x=6,y=0,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","LDMC"],na.rm=T)+0.024,label=expression(paste(bold("a"))),size=5)

plot_LDMC
# stat
lm1<-lm(LDMC~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


##all graphs for leaf structure

Leaf_structure<- ggarrange(plot_LMA, plot_LT, plot_LD, plot_LDMC, ncol = 2, nrow = 2, common.legend= TRUE, legend = "bottom")
Leaf_structure

ggsave(filename = "../results/leaf_structure.jpg", plot = Leaf_structure)
```

##leaf percentage loss
```{r}
# PLTdry
PLTdry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLT,fill=Metabolism))+
   geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Thickness"["dry"]," (%)")))+
  ylim(0,100)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  #ylab()+
  annotate("text",x=1,y=10,label=expression(paste(italic(bar("x"))," = 46.1")),size=4)+
  annotate("text",x=1,y=4,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=10,label=expression(paste("69.8")),size=4)+
  annotate("text",x=2,y=4,label=expression(paste("48")),size=4)+
  annotate("text",x=3,y=10,label=expression(paste("45.8")),size=4)+
  annotate("text",x=3,y=4,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=10,label=expression(paste("56.5")),size=4)+
  annotate("text",x=4,y=4,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=10,label=expression(paste("69.2")),size=4)+
  annotate("text",x=5,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=10,label=expression(paste("46.4")),size=4)+
  annotate("text",x=6,y=4,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLT"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLT"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLT"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLT"],na.rm=T)+8,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLT"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLT"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)

PLTdry_plot
# stat
lm1<-lm(D.PLT~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# PLAdry
PLAdry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLA,fill=Metabolism))+
   geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Area"["dry"]," (%)")))+
  ylim(10,90)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=21.2,label=expression(paste(italic(bar("x"))," = 49.4")),size=4)+
  annotate("text",x=1,y=16.4,label=expression(paste(italic("n")," = 48")),size=4)+
  annotate("text",x=2,y=21.2,label=expression(paste("43.7")),size=4)+
  annotate("text",x=2,y=16.4,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=21.2,label=expression(paste("45.8")),size=4)+
  annotate("text",x=3,y=16.4,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=21.2,label=expression(paste("60.2")),size=4)+
  annotate("text",x=4,y=16.4,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=21.2,label=expression(paste("53.0")),size=4)+
  annotate("text",x=5,y=16.4,label=expression(paste("41")),size=4)+
  annotate("text",x=6,y=21.2,label=expression(paste("63.1")),size=4)+
  annotate("text",x=6,y=16.4,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("bc"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("d"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("cd"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLA"],na.rm=T)+6.4,label=expression(paste(bold("a"))),size=5)

PLAdry_plot

# stat
lm1<-lm(D.PLA~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


# PLLedry
PLLedry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLLe,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Length"["dry"]," (%)")))+
  ylim(-15,20)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=-6,label=expression(paste(italic(bar("x"))," = 1.9")),size=4)+
  annotate("text",x=1,y=-8,label=expression(paste(italic("n")," = 41")),size=4)+
  annotate("text",x=2,y=-6,label=expression(paste("2.0")),size=4)+
  annotate("text",x=2,y=-8,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=-6,label=expression(paste("1.4")),size=4)+
  annotate("text",x=3,y=-8,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=-6,label=expression(paste("2.9")),size=4)+
  annotate("text",x=4,y=-8,label=expression(paste("39")),size=4)+
  annotate("text",x=5,y=-6,label=expression(paste("3.2")),size=4)+
  annotate("text",x=5,y=-8,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=-6,label=expression(paste("3.4")),size=4)+
  annotate("text",x=6,y=-8,label=expression(paste("41")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("bc"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("bc"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLLe"],na.rm=T)+3,label=expression(paste(bold("a"))),size=5)

PLLedry_plot
# stat
lm1<-lm(D.PLLe~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

# PLWidry (PLW1dry)
PLWdry_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLW1,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Width"["dry"]," (%)")))+
  ylim(0,100)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.position = "none",
        #legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=14,label=expression(paste(italic(bar("x"))," = 49.0")),size=4)+
  annotate("text",x=1,y=8,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=14,label=expression(paste("44.9")),size=4)+
  annotate("text",x=2,y=8,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=14,label=expression(paste("46.8")),size=4)+
  annotate("text",x=3,y=8,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=14,label=expression(paste("57.9")),size=4)+
  annotate("text",x=4,y=8,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=14,label=expression(paste("56.3")),size=4)+
  annotate("text",x=5,y=8,label=expression(paste("42")),size=4)+
  annotate("text",x=6,y=14,label=expression(paste("61.6")),size=4)+
  annotate("text",x=6,y=8,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("b"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLW1"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)

PLWdry_plot

# stat
lm1<-lm(D.PLW1~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


# PLV (PLW1dry)
PLV_plot<-ggplot(SRCdata,aes(x=Species,y=D.PLV,fill=Metabolism))+
  geom_boxplot(lwd=0.2,fatten=5)+
  theme_minimal()+
  scale_fill_manual(values=c("#E1BE6A", "#40B0A6"))+
   ggtitle(expression(paste("PL Volume"["dry"]," (%)")))+
  ylim(40,110)+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=13),
        plot.title = element_text(size = 20, hjust = 0.5))+
  annotate("text",x=1,y=50,label=expression(paste(italic(bar("x"))," = 71.6")),size=4)+
  annotate("text",x=1,y=45,label=expression(paste(italic("n")," = 49")),size=4)+
  annotate("text",x=2,y=50,label=expression(paste("82.5")),size=4)+
  annotate("text",x=2,y=45,label=expression(paste("46")),size=4)+
  annotate("text",x=3,y=50,label=expression(paste("70.5")),size=4)+
  annotate("text",x=3,y=45,label=expression(paste("38")),size=4)+
  annotate("text",x=4,y=50,label=expression(paste("82.7")),size=4)+
  annotate("text",x=4,y=45,label=expression(paste("41")),size=4)+
  annotate("text",x=5,y=50,label=expression(paste("85.3")),size=4)+
  annotate("text",x=5,y=45,label=expression(paste("41")),size=4)+
  annotate("text",x=6,y=50,label=expression(paste("80.2")),size=4)+
  annotate("text",x=6,y=45,label=expression(paste("42")),size=4)+
  annotate("text",x=1,y=max(SRCdata[SRCdata$Species=="Avsa","D.PLV"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=2,y=max(SRCdata[SRCdata$Species=="Hovu","D.PLV"],na.rm=T)+8,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=3,y=max(SRCdata[SRCdata$Species=="Trae","D.PLV"],na.rm=T)+8,label=expression(paste(bold("c"))),size=5)+
  annotate("text",x=4,y=max(SRCdata[SRCdata$Species=="Pegl","D.PLV"],na.rm=T)+8,label=expression(paste(bold("ab"))),size=5)+
  annotate("text",x=5,y=max(SRCdata[SRCdata$Species=="Zema","D.PLV"],na.rm=T)+8,label=expression(paste(bold("a"))),size=5)+
  annotate("text",x=6,y=max(SRCdata[SRCdata$Species=="Chga","D.PLV"],na.rm=T)+8,label=expression(paste(bold("b"))),size=5)

PLV_plot


# stat
lm1<-lm(D.PLV~Species,data=SRCdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

##all graphs for leaf structure

# Extract the legend
legend <- get_legend(
  PLV_plot +
    theme(legend.position = "right", text = element_text(size=20)) # Adjust position if needed
)

#legend <- plot(legend) #to check if it plots

#now remove the legend from the PLV plot
PLV_plot <- PLV_plot + theme(legend.position = "none")

Percent_loss_dry<- ggarrange(PLTdry_plot, PLAdry_plot, PLLedry_plot, PLWdry_plot, PLV_plot, legend, ncol =3, nrow = 2)

Percent_loss_dry

ggsave(filename = "../results/Percentloss_dry.jpg", plot = Percent_loss_dry, width = 12, height = 8)

```


## Scatterplots - LMA components

```{r}
# LMA, components ####

# Reorder Species factor
SRCdata$Species <- factor(SRCdata$Species, levels = c("Avsa", "Pegl" , "Trae", "Zema", "Hovu", "Chga"))

# LMA vs LT



LMA_LT<-ggplot(SRCdata,aes(x=T.LT,y=LMA,colour=Metabolism,shape=Species, lty = Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
   ylim(7,45)+
  xlim(0.06,0.31)+
  #geom_hline(yintercept=0,lty=2)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LMA (g m"^-2,")")))+
  xlab(expression(paste("LT (mm)")))+
  annotate("text",x=0.17,y=10,na.rm=T,label=expression(paste(italic("LT: P < 0.001, Sp: P < 0.001, LT x Sp: P = 0.347; R2 = 0.64 "))),size=3)


LMA_LT

# stat
lm1<-lm(LMA~T.LT*Species,data=SRCdata)
anova(lm1)
summary(lm1)

#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)

# LMA vs LD
LMA_LD<-ggplot(SRCdata,aes(x=LD,y=LMA,colour=Metabolism,shape=Species,lty=Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(7,45)+
  xlim(0.04,0.35)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LMA (g m"^-2,")")))+
  xlab(expression(paste("LD (g cm"^-3,")")))+
  annotate("text",x=0.17,y=10,na.rm=T,label=expression(paste(italic("LD: P < 0.001, Sp: P < 0.001, LD x Sp: P < 0.001; R2 = 0.67"))),size=3)

LMA_LD

# stat
lm1<-lm(LMA~LD*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph) #pairwise comparison: significant differences exist between certain species pairs, ex Pegl and Chga when compared to Avsa.For C3 species pairs like Hovu vs. Avsa and Trae vs. Avsa, there are no significant differences.

# LMA vs LDMC

LMA_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=LMA,colour=Metabolism,shape=Species,lty=Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(7,45)+
  xlim(0.04,0.23)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LMA (g m"^-2,")")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=0.14,y=10,na.rm=T,label=expression(paste(italic("LDMC: P < 0.001, Sp: P < 0.001, LDMC x Sp: P < 0.001; R2 = 0.80"))),size=3)


LMA_LDMC

# stat
lm1<-lm(LMA~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)

ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)

# LD vs LDMC

LD_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=LD,colour=Metabolism,shape=Species,lty=Species))+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(0.04,0.35)+
  xlim(0.04,0.23)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  geom_abline(intercept=0,slope=1,colour="darkgrey")+ #slope grey line 1:1
  ylab(expression(paste("LD (g cm"^-3,")")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=0.14,y=0.06,na.rm=T,label=expression(paste(italic("LDMC: P < 0.001, Sp: P < 0.001, LDMC x Sp: P < 0.001; R2 = 0.88"))),size=3)+
  annotate(geom = "text", x= 0.107, y=0.05, label= expression(paste(italic("grey line 1:1"))), size= 3)


LD_LDMC

# stat
lm1<-lm(LD~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)


# LT vs LD
LT_LD<-ggplot(SRCdata,aes(x=LD,y=T.LT,colour=Metabolism,shape=Species,lty=Species))+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  ylim(0.06,0.31)+
  xlim(0.04,0.35)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
    lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LT (mm)")))+
  xlab(expression(paste("LD (g cm"^-3,")")))+
  annotate("text",x=0.18,y=0.06,na.rm=T,label=expression(paste(italic("LD: P < 0.001, Sp: P < 0.001, LD x Sp: P < 0.001; R2 = 0.72"))),size=3)

LT_LD

# stat
lm1<-lm(T.LT~LD*Species,data=SRCdata)
anova(lm1)
summary(lm1)

ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)

# LT vs LDMC

LT_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=T.LT,colour=Metabolism,shape=Species,lty=Species))+
  ylim(0.06,0.31)+
  xlim(0.04,0.23)+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  ylab(expression(paste("LT (mm)")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))+
  annotate("text",x=0.13,y=0.06,na.rm=T,label=expression(paste(italic("LDMC: P = 0.114, Sp: P < 0.001, LDMC x Sp: P = 0.001; R2 = 0.73"))),size=3)

LT_LDMC

# stat
lm1<-lm(T.LT~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)


#all plot 

LMA_component <- ggarrange(LMA_LT, LMA_LD, LMA_LDMC, LD_LDMC, LT_LD, LT_LDMC, common.legend = T, legend = "bottom", ncol = 3, nrow = 2)

LMA_component 

ggsave(filename = "../results/LMA_component.jpg", plot = LMA_component , width = 13.5, height = 9)
```


# Shrinkage

```{r}
# PLV vs PLT dry
PLV_PLT_dry<-ggplot(SRCdata,aes(x=D.PLT,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,99)+
  xlim(10,90)+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=50,y=50,na.rm=T,label=expression(paste(italic("PLTdry: P < 0.001, Sp: P < 0.001, PLTdry x Sp: P < 0.001; R2 = 0.89"))),size=3)+
  xlab(expression(paste("PLT"[dry]," (%)")))+
  ylab(expression(paste("PLV"[dry]," (%)")))
  
PLV_PLT_dry 

# stat
lm1<-lm(D.PLV~D.PLT*Species,data=SRCdata)
anova(lm1)
summary(lm1)
ph<-glht(lm1,linfct=mcp(Species="Tukey"))
summary(ph)

y_avsa = 34.63947 + 0.80176 * 50 #correct
y_trae = 34.63947+9.32340 + (0.80176-0.22111)*50
y_hovu = 34.63947-9.73662 + (0.80176+0.02352 )*50
y_pegl = 34.63947+27.45534 + (0.80176-0.43615)*50
y_zema = 34.63947+14.99134 + (0.80176-0.28431)*50
y_chga = 34.63947+27.62275+(0.80176-0.41576 )*50

# PLV vs PLA dry
PLV_PLA_dry<-ggplot(SRCdata,aes(x=D.PLA,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,99)+
  xlim(20,80)+
 geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=50,y=50,na.rm=T,label=expression(paste(italic("PLAdry: P < 0.001, Sp: P < 0.001, PLAdry x Sp: P < 0.001; R2 = 0.78"))),size=3)+
  xlab(expression(paste("PLA"[dry]," (%)")))+
  ylab(expression(paste("PLV"[dry]," (%)")))

y_avsa = 20.54113 + 1.04091 * 50 #correct
y_trae = 20.54113+19.37115 + (1.04091-0.37224)*50
y_hovu = 20.54113+39.62089 + (1.04091-0.52901 )*50
y_pegl = 20.54113+39.94866 + (1.04091-0.67127)*50
y_zema = 20.54113+43.59089 + (1.04091-0.64025)*50
y_chga = 20.54113+23.08392+(1.04091-0.46169)*50

PLV_PLA_dry

# stat
lm1<-lm(D.PLV~D.PLA*Species,data=SRCdata)
anova(lm1)
summary(lm1)
#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)

#PLV_LD
PLV_LD<-ggplot(SRCdata,aes(x=LD,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,98)+
  xlim(0.04,0.35)+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=0.2,y=50,na.rm=T,label=expression(paste(italic("LD: P < 0.001, Sp: P < 0.001, LD x Sp: P < 0.001; R2 = 0.68"))),size=3)+
  ylab(expression(paste("PLV"[dry]," (%)")))+
  xlab(expression(paste("LD (g cm"^-3,")")))

PLV_LD

# stat
lm1<-lm(D.PLV~LD*Species,data=SRCdata)
anova(lm1)
summary(lm1)
#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)


#PLV  LDMC

PLV_LDMC<-ggplot(SRCdata,aes(x=LDMC,y=D.PLV,colour=Metabolism,shape=Species,lty=Species))+
  ylim(50,98)+
  xlim(0.04,0.23)+
  geom_point(size=2,aes(alpha=Species))+
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  scale_alpha_manual(values=c(1,0.6,0.3,1,0.6,0.3))+ 
  scale_shape_manual(values=c(0,15,2,16,1,17))+ #open for C3, closed for C4
  scale_linetype_manual(values=c(1,2,3,1,2,3))+
  geom_smooth(size=1.25,alpha=0.8,method=lm,se=F)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm')
        #legend.position = "none")+
  )+
  guides(shape = guide_legend(override.aes = list(size = 4)),  # Increase shape size in legend
  lty = guide_legend(override.aes = list(color = "black", size = 0.2)),  # Make line types black and smaller
  colour = guide_legend(ncol = 1))+
  annotate("text",x=0.13,y=50,na.rm=T,label=expression(paste(italic("LDMC: P < 0.001, Sp: P < 0.001, LDMC x Sp: P < 0.001; R2 = 0.76"))),size=3)+
  ylab(expression(paste("PLV"[dry]," (%)")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))

PLV_LDMC

# stat
lm1<-lm(D.PLV~LDMC*Species,data=SRCdata)
anova(lm1)
summary(lm1)
#ph<-glht(lm1,linfct=mcp(Species="Tukey"))
#summary(ph)

#all plot 

Shrinkage_component <- ggarrange(PLV_PLT_dry, PLV_PLA_dry ,PLV_LD, PLV_LDMC, common.legend = T, legend = "bottom", ncol = 2, nrow = 2)

Shrinkage_component 

ggsave(filename = "../results/Shrinkage_component.jpg", plot = Shrinkage_component , width = 10, height = 7)


```

# SRC, dehydration/rehydration analysis 

F for after dehydration or fresh -- STAGE 2
R for Rehydration -- STAGE 3

```{r}
# all species, facet ####
# FvFm

SRCdata$F.FvFm <- as.numeric(SRCdata$F.FvFm)
SRCdata$R.FvFm <- as.numeric(SRCdata$R.FvFm)
SRCdata <- SRCdata %>%
  mutate(Name = case_when(
    Species =="Avsa" ~ "A. sativa",
    Species =="Hovu"~ "H. vulgare",
    Species =="Trae"~ "T. aestivum",
    Species =="Zema"~ "Z. mays",
    Species =="Pegl"~ "P. glaucum",
    Species == "Chga"~"C. gayan"))

SRCdata$Name<- as.factor(SRCdata$Name)
SRCdata$Metabolism <- as.factor(SRCdata$Metabolism)


# "Avsa"
data_subset_avsa <- SRCdata[SRCdata$Species == "Avsa", ]

Avsa <- ggplot(data=data_subset_avsa, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("A. sativa")

# "Hovu"
data_subset_Hovu <- SRCdata[SRCdata$Species == "Hovu", ]

Hovu <- ggplot(data=data_subset_Hovu, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("H. vulgare")


# "Trae"
data_subset_Trae <- SRCdata[SRCdata$Species == "Trae", ]

Trae <- ggplot(data=data_subset_Trae, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("T. aestivum")

# "Pegl"
data_subset_Pegl <- SRCdata[SRCdata$Species == "Pegl", ]

Pegl <- ggplot(data=data_subset_Pegl, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("P. glaucum")

# "Chla"
data_subset_Chga <- SRCdata[SRCdata$Species == "Chga", ]

Chga <- ggplot(data=data_subset_Chga, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("C. gayan")


# "Zema"
data_subset_Zema <- SRCdata[SRCdata$Species == "Zema", ]

Zema <- ggplot(data=data_subset_Zema, aes(x=F.FvFm, y=R.FvFm, colour=Metabolism)) +
  geom_point(size=3) +
  scale_colour_manual(values=c("#40B0A6")) +
  geom_abline(intercept=0, slope=1, colour="darkgrey") +
  geom_smooth(aes(x=F.FvFm,y=R.FvFm, colour= Metabolism), fill="grey") +
  scale_y_continuous(limits=c(-0.25, 0.8), breaks=c(0, 0.25, 0.5, 0.75)) +
  scale_x_continuous(limits=c(0, 0.8), breaks=c(0, 0.25, 0.5, 0.7)) +
  theme_minimal() +
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        legend.position = "none",
        title = element_text(face = "bold.italic")) +
  ylab(expression(paste("F"[v], "/F"[m], " upon rehydration - stage 3"))) +
  xlab(expression(paste("F"[v], "/F"[m], "dehydration - stage 2"))) +
  ggtitle("Z. mays")

FVFM_plot <- ggarrange(Avsa, Trae, Hovu, Pegl, Chga, Zema, ncol = 3, nrow = 2)

ggsave(filename = "../results/FVFM_dehydration_rehydration.jpg", plot = FVFM_plot , width = 10, height = 7)

```

#RWC and water potential

I really don't have the same graph as Miquel... why?

```{r}
# water potential - 'mean'
SRCdata$WPleaf2 <- as.numeric(SRCdata$WPleaf2)

g1<-ggplot(data=SRCdata,aes(x=F.RWC,y=WPleaf2))+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_point(size=3,shape=21,fill="black",alpha=0.5)+
  geom_smooth(aes(x=F.RWC,y=WPleaf2),color="black",fill="grey")+
  #scale_y_continuous(limits=c(-0.25,0.8),breaks=c(0,0.25,0.5,0.75))+
  scale_x_continuous(limits=c(0,100))+
  #xlim(0,1)+
  facet_wrap(~Species,ncol=3)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13,face="italic"))+
  ylab(expression(paste(Psi["leaf"]," (MPa)")))+
  xlab(expression(paste("RWC (%)")))

```

#RWC PLRC
```{r}
# data per species, FvFm, PLRC ####
SRCdata$F.RWC <- as.numeric(SRCdata$F.RWC)
SRCdata$F.FvFm <- as.numeric(SRCdata$F.FvFm)
SRCdata$T.FvFm <- as.numeric(SRCdata$T.FvFm)
SRCdata$R.FvFm <- as.numeric(SRCdata$R.FvFm)
SRCdata$PLRC

# Avsa ----

SRCdata_avsa <- SRCdata %>% filter(Species== "Avsa")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_avsa$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_avsa)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_avsa, start = start)
summary(model)

plot(SRCdata_avsa$F.RWC, SRCdata_avsa$PLRC)
lines(SRCdata_avsa$F.RWC, predict(model, list(x = SRCdata_avsa$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.avsa <- seq(min(SRCdata_avsa$F.RWC,na.rm =T ), max(SRCdata_avsa$F.RWC, na.rm = T), length.out = length(SRCdata_avsa$F.RWC))
y_model.avsa <-  90.687433   * exp(-0.036148   * x_seq.avsa ) -5.710108

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
avsa_10= (1/-0.036148) * (log(10+5.710108) - log(90.687433))
avsa_50= (1/-0.036148) * (log(50+5.710108) - log(90.687433))

Avsa_PLRC<-ggplot(SRCdata_avsa,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_avsa,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.avsa, y = y_model.avsa), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=avsa_10,color="blue",lty=3)+
  geom_vline(xintercept=avsa_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("A. sativa")+
  geom_rect(data=data.frame(xmin=16,xmax=75,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),alpha=0.05,fill="royalblue",inherit.aes=F) #shaded blue area denotes embolism events according to OV method
Avsa_PLRC




# Hovu -----
SRCdata_hovu <- SRCdata %>% filter(Species== "Hovu")
# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_hovu$PLRC, na.rm = T) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_hovu)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_hovu, start = start)
summary(model)

plot(SRCdata_hovu$F.RWC, SRCdata_hovu$PLRC)
lines(SRCdata_hovu$F.RWC, predict(model, list(x = SRCdata_hovu$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.hovu <- seq(min(SRCdata_hovu$F.RWC,na.rm =T ), max(SRCdata_hovu$F.RWC, na.rm = T), length.out = length(SRCdata_hovu$F.RWC))
y_model.hovu <-  102.21313   * exp(-0.03123    * x_seq.hovu ) -6.81649

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
hovu_10= (1/-0.03123) * (log(10+6.81649) - log(102.21313))
hovu_50= (1/-0.03123) * (log(50+6.81649) - log(102.21313))

hovu_PLRC<-ggplot(SRCdata_hovu,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_hovu,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.hovu, y = y_model.hovu), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=hovu_10,color="blue",lty=3)+
  geom_vline(xintercept=hovu_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("H. vulgare")+
  geom_rect(data=data.frame(xmin=22,xmax=74,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=23,xmax=60,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=19,xmax=74,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)
hovu_PLRC


# Trae -----
SRCdata_trae <- SRCdata %>% filter(Species== "Trae")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_trae$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_trae)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_trae, start = start)
summary(model)

plot(SRCdata_trae$F.RWC, SRCdata_trae$PLRC)
lines(SRCdata_trae$F.RWC, predict(model, list(x = SRCdata_trae$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.trae <- seq(min(SRCdata_trae$F.RWC,na.rm =T ), max(SRCdata_trae$F.RWC, na.rm = T), length.out = length(SRCdata_trae$F.RWC))
y_model.trae <-  73.578960   * exp(-0.012623   * x_seq.trae ) -21.445047

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
trae_10= (1/-0.012623) * (log(10+21.445047) - log(73.578960))
trae_50= (1/-0.012623) * (log(50+21.445047) - log(73.578960))

trae_PLRC<-ggplot(SRCdata_trae,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_trae,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.trae, y = y_model.trae), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=trae_10,color="blue",lty=3)+
  geom_vline(xintercept=trae_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("T. aestivum")+
  geom_rect(data=data.frame(xmin=11.5,xmax=61.5,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=23,xmax=70,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=44,xmax=72,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
trae_PLRC



# Pegl ----
SRCdata_Pegl <- SRCdata %>% filter(Species== "Pegl")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Pegl$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_Pegl)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Pegl, start = start)
summary(model)

plot(SRCdata_Pegl$F.RWC, SRCdata_Pegl$PLRC)
lines(SRCdata_Pegl$F.RWC, predict(model, list(x = SRCdata_Pegl$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Pegl <- seq(min(SRCdata_Pegl$F.RWC,na.rm =T ), max(SRCdata_Pegl$F.RWC, na.rm = T), length.out = length(SRCdata_Pegl$F.RWC))
y_model.Pegl <-  88.052445   * exp(-0.024293   * x_seq.Pegl )-10.882535

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Pegl_10= (1/-0.024293) * (log(10+10.882535) - log(88.052445))
Pegl_50= (1/-0.024293) * (log(50+10.882535) - log(88.052445))

Pegl_PLRC<-ggplot(SRCdata_Pegl,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_Pegl,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  geom_line(aes(x = x_seq.Pegl, y = y_model.Pegl), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=Pegl_10,color="blue",lty=3)+
  geom_vline(xintercept=Pegl_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("P. glaucum")+
  geom_rect(data=data.frame(xmin=7,xmax=9,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=20,xmax=30,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Pegl_PLRC


# Zema -----
SRCdata_Zema <- SRCdata %>% filter(Species== "Zema")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Zema$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_Zema)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Zema, start = start)
summary(model)

plot(SRCdata_Zema$F.RWC, SRCdata_Zema$PLRC)
lines(SRCdata_Zema$F.RWC, predict(model, list(x = SRCdata_Zema$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Zema <- seq(min(SRCdata_Zema$F.RWC,na.rm =T ), max(SRCdata_Zema$F.RWC, na.rm = T), length.out = length(SRCdata_Zema$F.RWC))
y_model.Zema <-  125.602294   * exp(-0.009158   * x_seq.Zema )-53.577050

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Zema_10= (1/-0.009158) * (log(10+53.577050) - log(125.602294))
Zema_50= (1/-0.009158) * (log(50+53.577050) - log(125.602294))

Zema_PLRC<-ggplot(SRCdata_Zema,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_Zema,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  geom_line(aes(x = x_seq.Zema, y = y_model.Zema), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=Zema_10,color="blue",lty=3)+
  geom_vline(xintercept=Zema_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("Z. mays")+
  geom_rect(data=data.frame(xmin=4,xmax=5,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=11,xmax=35,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Zema_PLRC

# Chga----
SRCdata_Chga <- SRCdata %>% filter(Species== "Chga")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Chga$PLRC) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLRC - theta.0) ~ F.RWC, data=SRCdata_Chga)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLRC ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Chga, start = start)
summary(model)

plot(SRCdata_Chga$F.RWC, SRCdata_Chga$PLRC)
lines(SRCdata_Chga$F.RWC, predict(model, list(x = SRCdata_Chga$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Chga <- seq(min(SRCdata_Chga$F.RWC,na.rm =T ), max(SRCdata_Chga$F.RWC, na.rm = T), length.out = length(SRCdata_Chga$F.RWC))
y_model.Chga <-  125.602294   * exp(-0.009158   * x_seq.Chga )-53.577050

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Chga_10= (1/-0.009158) * (log(10+53.577050) - log(125.602294))
Chga_50= (1/-0.009158) * (log(50+53.577050) - log(125.602294))

Chga_PLRC<-ggplot(SRCdata_Chga,aes(x=F.RWC,y=PLRC))+
  geom_point(data=SRCdata_Chga,aes(x=F.RWC,y=PLRC, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  geom_line(aes(x = x_seq.Chga, y = y_model.Chga), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=Chga_10,color="blue",lty=3)+
  geom_vline(xintercept=Chga_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of rehydration capacity (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("C. gayan")+
  geom_rect(data=data.frame(xmin=9,xmax=10,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=9,xmax=10,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=7,xmax=40,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Chga_PLRC

### all plots ----
PLRC_RWC_plot <- ggarrange(Avsa_PLRC, hovu_PLRC, trae_PLRC, Pegl_PLRC, Zema_PLRC, Chga_PLRC, ncol =3, nrow = 2)

PLRC_RWC_plot 

ggsave(filename = "../results/PLRC_RWC_plot .jpg", plot = PLRC_RWC_plot, width = 12, height = 8)

```


#RWC FVFM - PLCF
```{r}
# data per species, FvFm ####
SRCdata$F.RWC <- as.numeric(SRCdata$F.RWC)
SRCdata$F.FvFm <- as.numeric(SRCdata$F.FvFm)
SRCdata$T.FvFm <- as.numeric(SRCdata$T.FvFm)
SRCdata$R.FvFm <- as.numeric(SRCdata$R.FvFm)



# Avsa ----

SRCdata_avsa <- SRCdata %>% filter(Species== "Avsa")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_avsa$PLCF) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLCF - theta.0) ~ F.RWC, data=SRCdata_avsa)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLCF ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_avsa, start = start)
summary(model)

plot(SRCdata_avsa$F.RWC, SRCdata_avsa$PLCF)
lines(SRCdata_avsa$F.RWC, predict(model, list(x = SRCdata_avsa$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.avsa <- seq(min(SRCdata_avsa$F.RWC,na.rm =T ), max(SRCdata_avsa$F.RWC, na.rm = T), length.out = length(SRCdata_avsa$F.RWC))
y_model.avsa <-  90.687433   * exp(-0.036148   * x_seq.avsa ) -5.710108

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
#avsa_10= (1/-0.036148) * (log(10+5.710108) - log(90.687433))
#avsa_50= (1/-0.036148) * (log(50+5.710108) - log(90.687433))

Avsa_PLCF<-ggplot(SRCdata_avsa,aes(x=F.RWC,y=PLCF))+
  geom_point(data=SRCdata_avsa,aes(x=F.RWC,y=PLCF, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  #geom_line(aes(x = x_seq.avsa, y = y_model.avsa), color = 'black', size=2, alpha=0.7)+
  #geom_vline(xintercept=avsa_10,color="blue",lty=3)+
  #geom_vline(xintercept=avsa_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of chlorophyll fluoresence (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("A. sativa")+
  geom_rect(data=data.frame(xmin=16,xmax=75,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),alpha=0.05,fill="royalblue",inherit.aes=F) #shaded blue area denotes embolism events according to OV method
Avsa_PLCF




# Hovu -----
SRCdata_hovu <- SRCdata %>% filter(Species== "Hovu")
# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_hovu$PLCF, na.rm = T) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLCF - theta.0) ~ F.RWC, data=SRCdata_hovu)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLCF ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_hovu, start = start)
summary(model)

plot(SRCdata_hovu$F.RWC, SRCdata_hovu$PLCF)

#output model
x_seq.hovu <- seq(min(SRCdata_hovu$F.RWC,na.rm =T ), max(SRCdata_hovu$F.RWC, na.rm = T), length.out = length(SRCdata_hovu$F.RWC))
y_model.hovu <-  140.727909   * exp(-0.029974    * x_seq.hovu ) -8.513784

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
hovu_10= (1/-0.029974) * (log(10+8.513784) - log(140.727909))
hovu_50= (1/-0.029974) * (log(50+8.513784) - log(140.727909))

hovu_PLCF<-ggplot(SRCdata_hovu,aes(x=F.RWC,y=PLCF))+
  geom_point(data=SRCdata_hovu,aes(x=F.RWC,y=PLCF, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  geom_line(aes(x = x_seq.hovu, y = y_model.hovu), color = 'black', size=2, alpha=0.7)+
  geom_vline(xintercept=hovu_10,color="blue",lty=3)+
  geom_vline(xintercept=hovu_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of chlorophyll fluoresence (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("H. vulgare")+
  geom_rect(data=data.frame(xmin=22,xmax=74,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=23,xmax=60,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=19,xmax=74,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
    alpha=0.05,fill="royalblue",inherit.aes=F)
hovu_PLCF


# Trae -----
SRCdata_trae <- SRCdata %>% filter(Species== "Trae")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_trae$PLCF) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLCF - theta.0) ~ F.RWC, data=SRCdata_trae)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLCF ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_trae, start = start)
summary(model)

plot(SRCdata_trae$F.RWC, SRCdata_trae$PLCF)
lines(SRCdata_trae$F.RWC, predict(model, list(x = SRCdata_trae$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.trae <- seq(min(SRCdata_trae$F.RWC,na.rm =T ), max(SRCdata_trae$F.RWC, na.rm = T), length.out = length(SRCdata_trae$F.RWC))
y_model.trae <-  73.578960   * exp(-0.012623   * x_seq.trae ) -21.445047

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
trae_10= (1/-0.012623) * (log(10+21.445047) - log(73.578960))
trae_50= (1/-0.012623) * (log(50+21.445047) - log(73.578960))

trae_PLCF<-ggplot(SRCdata_trae,aes(x=F.RWC,y=PLCF))+
  geom_point(data=SRCdata_trae,aes(x=F.RWC,y=PLCF, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#E1BE6A")) +
  #geom_line(aes(x = x_seq.trae, y = y_model.trae), color = 'black', size=2, alpha=0.7)+
  #geom_vline(xintercept=trae_10,color="blue",lty=3)+
  #geom_vline(xintercept=trae_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of chlorophyll fluoresence (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("T. aestivum")+
  geom_rect(data=data.frame(xmin=11.5,xmax=61.5,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=23,xmax=70,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=44,xmax=72,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
trae_PLCF



# Pegl ----
SRCdata_Pegl <- SRCdata %>% filter(Species== "Pegl")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Pegl$PLCF) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLCF - theta.0) ~ F.RWC, data=SRCdata_Pegl)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLCF ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Pegl, start = start)
summary(model)

plot(SRCdata_Pegl$F.RWC, SRCdata_Pegl$PLCF)
lines(SRCdata_Pegl$F.RWC, predict(model, list(x = SRCdata_Pegl$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Pegl <- seq(min(SRCdata_Pegl$F.RWC,na.rm =T ), max(SRCdata_Pegl$F.RWC, na.rm = T), length.out = length(SRCdata_Pegl$F.RWC))
y_model.Pegl <-  88.052445   * exp(-0.024293   * x_seq.Pegl )-10.882535

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Pegl_10= (1/-0.024293) * (log(10+10.882535) - log(88.052445))
Pegl_50= (1/-0.024293) * (log(50+10.882535) - log(88.052445))

Pegl_PLCF<-ggplot(SRCdata_Pegl,aes(x=F.RWC,y=PLCF))+
  geom_point(data=SRCdata_Pegl,aes(x=F.RWC,y=PLCF, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  #geom_line(aes(x = x_seq.Pegl, y = y_model.Pegl), color = 'black', size=2, alpha=0.7)+
  #geom_vline(xintercept=Pegl_10,color="blue",lty=3)+
  #geom_vline(xintercept=Pegl_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of chlorophyll fluoresence (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("P. glaucum")+
  geom_rect(data=data.frame(xmin=7,xmax=9,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=20,xmax=30,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Pegl_PLCF


# Zema -----
SRCdata_Zema <- SRCdata %>% filter(Species== "Zema")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Zema$PLCF) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLCF - theta.0) ~ F.RWC, data=SRCdata_Zema)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLCF ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Zema, start = start)
summary(model)

plot(SRCdata_Zema$F.RWC, SRCdata_Zema$PLCF)
lines(SRCdata_Zema$F.RWC, predict(model, list(x = SRCdata_Zema$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Zema <- seq(min(SRCdata_Zema$F.RWC,na.rm =T ), max(SRCdata_Zema$F.RWC, na.rm = T), length.out = length(SRCdata_Zema$F.RWC))
y_model.Zema <-  125.602294   * exp(-0.009158   * x_seq.Zema )-53.577050

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Zema_10= (1/-0.009158) * (log(10+53.577050) - log(125.602294))
Zema_50= (1/-0.009158) * (log(50+53.577050) - log(125.602294))

Zema_PLCF<-ggplot(SRCdata_Zema,aes(x=F.RWC,y=PLCF))+
  geom_point(data=SRCdata_Zema,aes(x=F.RWC,y=PLCF, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  #geom_line(aes(x = x_seq.Zema, y = y_model.Zema), color = 'black', size=2, alpha=0.7)+
  #geom_vline(xintercept=Zema_10,color="blue",lty=3)+
  #geom_vline(xintercept=Zema_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of chlorophyll fluoresence (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("Z. mays")+
  geom_rect(data=data.frame(xmin=4,xmax=5,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=11,xmax=35,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Zema_PLCF

# Chga----
SRCdata_Chga <- SRCdata %>% filter(Species== "Chga")
#find best fit model
#E(y)=ex+
#help from https://rpubs.com/mengxu/exponential-model
#constant thetha = 0 because data as x increases is 0~, thetha is the stabilizing trend over as x increases.

# Select an approximate $\theta$, since theta must be lower than min(y), and greater than zero
theta.0 <- min(SRCdata_Chga$PLCF) * 0.5  

# Estimate the rest parameters using a linear model
model.0 <- lm(log(PLCF - theta.0) ~ F.RWC, data=SRCdata_Chga)  
alpha.0 <- exp(coef(model.0)[1])
beta.0 <- coef(model.0)[2]

# Starting parameters
start <- list(alpha = alpha.0, beta = beta.0, theta = theta.0)
start

model <- nls(PLCF ~ alpha * exp(beta * F.RWC) + theta , data = SRCdata_Chga, start = start)
summary(model)

plot(SRCdata_Chga$F.RWC, SRCdata_Chga$PLCF)
lines(SRCdata_Chga$F.RWC, predict(model, list(x = SRCdata_Chga$F.RWC)), col = 'skyblue', lwd = 3)

#output model
x_seq.Chga <- seq(min(SRCdata_Chga$F.RWC,na.rm =T ), max(SRCdata_Chga$F.RWC, na.rm = T), length.out = length(SRCdata_Chga$F.RWC))
y_model.Chga <-  125.602294   * exp(-0.009158   * x_seq.Chga )-53.577050

# Calculate the relative water content associated with 10% and 50% losses of rehydration capacity
Chga_10= (1/-0.009158) * (log(10+53.577050) - log(125.602294))
Chga_50= (1/-0.009158) * (log(50+53.577050) - log(125.602294))

Chga_PLCF<-ggplot(SRCdata_Chga,aes(x=F.RWC,y=PLCF))+
  geom_point(data=SRCdata_Chga,aes(x=F.RWC,y=PLCF, colour= Metabolism),size=3,alpha=0.5)+
  scale_colour_manual(values=c("#40B0A6")) +
  #geom_line(aes(x = x_seq.Chga, y = y_model.Chga), color = 'black', size=2, alpha=0.7)+
  #geom_vline(xintercept=Chga_10,color="blue",lty=3)+
  #geom_vline(xintercept=Chga_50,color="red",lty=3)+
  ylim(-0.25,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Percent loss of chlorophyll fluoresence (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("C. gayan")+
  geom_rect(data=data.frame(xmin=9,xmax=10,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=9,xmax=10,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)+
  geom_rect(data=data.frame(xmin=7,xmax=40,ymin=0,ymax=100),aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),
            alpha=0.05,fill="royalblue",inherit.aes=F)
Chga_PLCF

### all plots ----
PLCF_RWC_plot <- ggarrange(Avsa_PLCF, hovu_PLCF, trae_PLCF, Pegl_PLCF, Zema_PLCF, Chga_PLCF, ncol =3, nrow = 2)

PLCF_RWC_plot 

ggsave(filename = "../results/PLCF_RWC_plot .jpg", plot = PLCF_RWC_plot, width = 12, height = 8)


```

#Shrinkage
```{r}


# 
# Avsa
Avsa_shrinkage<-ggplot()+
    geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLV),size=2,alpha=0.5,fill="#e05a12")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLV),color="#e05a12",fill="#e05a12")+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLT),size=2,alpha=0.5,fill="#6fe012")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLT),color="#6fe012",fill="#6fe012")+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLA),size=2,alpha=0.5,fill="#1295e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLA),color="#1295e0",fill="#1295e0")+
  geom_point(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLW1),size=2,alpha=0.5,fill="white",colour="#9512e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Avsa",],aes(x=F.RWC,y=F.PLW1),color="#9512e0",fill="#9512e0")+
  ylim(-10,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Leaf shrinkage (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("A. sativa")
Avsa_shrinkage

# Hovu
Hovu_shrinkage<-ggplot()+
    geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLV),size=2,alpha=0.5,fill="#e05a12")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLV),color="#e05a12",fill="#e05a12")+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLT),size=2,alpha=0.5,fill="#6fe012")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLT),color="#6fe012",fill="#6fe012")+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLA),size=2,alpha=0.5,fill="#1295e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLA),color="#1295e0",fill="#1295e0")+
  geom_point(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLW1),size=2,alpha=0.5,fill="white",colour="#9512e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Hovu",],aes(x=F.RWC,y=F.PLW1),color="#9512e0",fill="#9512e0")+
  ylim(-10,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Leaf shrinkage (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("H. vulgare")
Hovu_shrinkage

# Trae
Trae_shrinkage<-ggplot()+
    geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLV),size=2,alpha=0.5,fill="#e05a12")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLV),color="#e05a12",fill="#e05a12")+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLT),size=2,alpha=0.5,fill="#6fe012")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLT),color="#6fe012",fill="#6fe012")+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLA),size=2,alpha=0.5,fill="#1295e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLA),color="#1295e0",fill="#1295e0")+
  geom_point(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLW1),size=2,alpha=0.5,fill="white",colour="#9512e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Trae",],aes(x=F.RWC,y=F.PLW1),color="#9512e0",fill="#9512e0")+
  ylim(-10,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Leaf shrinkage (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("T. aestivum")
Trae_shrinkage



# Pegl
Pegl_shrinkage<-ggplot()+
    geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLV),size=2,alpha=0.5,fill="#e05a12")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLV),color="#e05a12",fill="#e05a12")+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLT),size=2,alpha=0.5,fill="#6fe012")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLT),color="#6fe012",fill="#6fe012")+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLA),size=2,alpha=0.5,fill="#1295e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLA),color="#1295e0",fill="#1295e0")+
  geom_point(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLW1),size=2,alpha=0.5,fill="white",colour="#9512e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Pegl",],aes(x=F.RWC,y=F.PLW1),color="#9512e0",fill="#9512e0")+
  ylim(-10,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Leaf shrinkage (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("P. glaucum")
Pegl_shrinkage


# Zema
Zema_shrinkage<-ggplot()+
    geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLV),size=2,alpha=0.5,fill="#e05a12")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLV),color="#e05a12",fill="#e05a12")+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLT),size=2,alpha=0.5,fill="#6fe012")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLT),color="#6fe012",fill="#6fe012")+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLA),size=2,alpha=0.5,fill="#1295e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLA),color="#1295e0",fill="#1295e0")+
  geom_point(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLW1),size=2,alpha=0.5,fill="white",colour="#9512e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Zema",],aes(x=F.RWC,y=F.PLW1),color="#9512e0",fill="#9512e0")+
  ylim(-10,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Leaf shrinkage (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("Z. mays")
Zema_shrinkage


# Chga
Chga_shrinkage<-ggplot()+
    geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLV),size=2,alpha=0.5,fill="#e05a12")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLV),color="#e05a12",fill="#e05a12")+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLT),size=2,alpha=0.5,fill="#6fe012")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLT),color="#6fe012",fill="#6fe012")+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLA),size=2,alpha=0.5,fill="#1295e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLA),color="#1295e0",fill="#1295e0")+
  geom_point(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLW1),size=2,alpha=0.5,fill="white",colour="#9512e0")+
  geom_smooth(data=SRCdata[SRCdata$Species=="Chga",],aes(x=F.RWC,y=F.PLW1),color="#9512e0",fill="#9512e0")+
  ylim(-10,100)+
  xlim(0,100)+
  theme_minimal()+
  theme(axis.title.y=element_blank(),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13, face="italic"),
        title = element_text(face = "bold.italic"),
        legend.position = "none") +
  ylab(expression(paste("Leaf shrinkage (%)")))+
  xlab(expression(paste("Relative water content (%)")))+
  ggtitle("C. gayan")
Chga_shrinkage


### all plots ----
shrinkage_RWC_plot <- ggarrange(Avsa_shrinkage, Hovu_shrinkage, Trae_shrinkage, Pegl_shrinkage, Zema_shrinkage, Chga_shrinkage, ncol =3, nrow = 2)

shrinkage_RWC_plot 

ggsave(filename = "../results/shrinkage_RWC_plot .jpg", plot = shrinkage_RWC_plot, width = 12, height = 8)

```

#PV data

```{r}
### PV, data loading, variable calculation, means ####

PVdata<-read_xlsx(path = "../data/C3C4 Grasses - PV.xlsx", sheet = "C3C4G PV R")

PVdata$Metabolism<-factor(PVdata$Metabolism)
PVdata$Species<-factor(PVdata$Species,levels=c("Avsa","Hovu","Trae","Pegl","Zema","Chga"))

# variable calculation
# For each leaf, leaf area T.LA and thickness T.LT were measured along the PV curve and at the dry stage D.LA, D.LT for calculating the percentage loss of thickness PLT and area PLAat turgor loss point and in a dry leaf 
PVdata$tlp.PLT<-100-PVdata$tlp.LT/PVdata$T.LT*100
PVdata$D.PLT<-100-PVdata$D.LT/PVdata$T.LT*100

PVdata$tlp.PLA<-100-PVdata$tlp.LA/PVdata$T.LA*100
PVdata$D.PLA<-100-PVdata$D.LA/PVdata$T.LA*100

PVdata$T.LV<-PVdata$T.LA*PVdata$T.LT/10
PVdata$tlp.LV<-PVdata$tlp.LA*PVdata$tlp.LT/10
PVdata$D.LV<-PVdata$D.LA*PVdata$D.LT/10

PVdata$tlp.PLV<-100-PVdata$tlp.LV/PVdata$T.LV*100
PVdata$D.PLV<-100-PVdata$D.LV/PVdata$T.LV*100

#leaf saturated water content, LMA, density, LDMC, capacitance at full turgor and at turgor loss point (Cft and Ctlp). leaf-specific capacitances (C*) were obtained on both area and dry mass basis. bulk modulus of elasticity from total water content: --> The bulk modulus of elasticity from symplast water content () was calculated as  = * (1af), following Bartlett et al (2012). The fraction of apoplastic water (af) was calculated as the 1x intercept in the 1/ vs 1RWC relationship
PVdata$SWCm<-(PVdata$TW-PVdata$DW)/PVdata$DW #?
PVdata$LMA<-PVdata$DW/1000/(PVdata$T.LA/10000)
PVdata$LD<-PVdata$DW/1000/PVdata$T.LV
PVdata$LDMC<-PVdata$DW/PVdata$TW
PVdata$SWCpv<-PVdata$SWpv/PVdata$DW #?
PVdata$cft.mass<-PVdata$cft*PVdata$SWpv/PVdata$DW*1000
PVdata$cft.area<-PVdata$cft.mass/PVdata$LMA
PVdata$ctlp.mass<-PVdata$ctlp*PVdata$SWpv/PVdata$DW*1000
PVdata$ctlp.area<-PVdata$ctlp.mass/PVdata$LMA
PVdata$em<-PVdata$em.*(1-PVdata$af)

# means
m.PVdata<-ddply(PVdata,c("Species","Metabolism"),summarise,
            m.SWCpv=mean(SWCpv,na.rm=TRUE),n.SWCpv=sum(!is.na(SWCpv)),se.SWCpv=sd(SWCpv,na.rm=T)/sqrt(n.SWCpv),
            m.rwc.tlp=mean(rwc.tlp,na.rm=TRUE),n.rwc.tlp=sum(!is.na(rwc.tlp)),se.rwc.tlp=sd(rwc.tlp,na.rm=T)/sqrt(n.rwc.tlp),
            m.osp.tlp=mean(osp.tlp,na.rm=TRUE),n.osp.tlp=sum(!is.na(osp.tlp)),se.osp.tlp=sd(osp.tlp,na.rm=T)/sqrt(n.osp.tlp),
            m.osp.ft=mean(osp.ft,na.rm=TRUE),n.osp.ft=sum(!is.na(osp.ft)),se.osp.ft=sd(osp.ft,na.rm=T)/sqrt(n.osp.ft),
            m.em.=mean(em.,na.rm=TRUE),n.em.=sum(!is.na(em.)),se.em.=sd(em.,na.rm=T)/sqrt(n.em.),
            m.em=mean(em,na.rm=TRUE),n.em=sum(!is.na(em)),se.em=sd(em,na.rm=T)/sqrt(n.em),
            m.af=mean(af,na.rm=TRUE),n.af=sum(!is.na(af)),se.af=sd(af,na.rm=T)/sqrt(n.af),
            m.cft=mean(cft,na.rm=TRUE),n.cft=sum(!is.na(cft)),se.cft=sd(cft,na.rm=T)/sqrt(n.cft),
            m.ctlp=mean(ctlp,na.rm=TRUE),n.ctlp=sum(!is.na(ctlp)),se.ctlp=sd(ctlp,na.rm=T)/sqrt(n.ctlp),
            m.cft.area=mean(cft.area,na.rm=TRUE),n.cft.area=sum(!is.na(cft.area)),se.cft.area=sd(cft.area,na.rm=T)/sqrt(n.cft.area),
            m.cft.mass=mean(cft.mass,na.rm=TRUE),n.cft.mass=sum(!is.na(cft.mass)),se.cft.mass=sd(cft.mass,na.rm=T)/sqrt(n.cft.mass),
            m.ctlp.area=mean(ctlp.area,na.rm=TRUE),n.ctlp.area=sum(!is.na(ctlp.area)),se.ctlp.area=sd(ctlp.area,na.rm=T)/sqrt(n.ctlp.area),
            m.ctlp.mass=mean(ctlp.mass,na.rm=TRUE),n.ctlp.mass=sum(!is.na(ctlp.mass)),se.ctlp.mass=sd(ctlp.mass,na.rm=T)/sqrt(n.ctlp.mass),
            m.LMA=mean(LMA,na.rm=TRUE),n.LMA=sum(!is.na(LMA)),se.LMA=sd(LMA,na.rm=T)/sqrt(n.LMA),
            m.T.LT=mean(T.LT,na.rm=TRUE),n.T.LT=sum(!is.na(T.LT)),se.T.LT=sd(T.LT,na.rm=T)/sqrt(n.T.LT),
            m.LD=mean(LD,na.rm=TRUE),n.LD=sum(!is.na(LD)),se.LD=sd(LD,na.rm=T)/sqrt(n.LD),
            m.tlp.PLT=mean(tlp.PLT,na.rm=TRUE),n.tlp.PLT=sum(!is.na(tlp.PLT)),se.tlp.PLT=sd(tlp.PLT,na.rm=T)/sqrt(n.tlp.PLT),
            m.D.PLT=mean(D.PLT,na.rm=TRUE),n.D.PLT=sum(!is.na(D.PLT)),se.D.PLT=sd(D.PLT,na.rm=T)/sqrt(n.D.PLT),
            m.tlp.PLA=mean(tlp.PLA,na.rm=TRUE),n.tlp.PLA=sum(!is.na(tlp.PLA)),se.tlp.PLA=sd(tlp.PLA,na.rm=T)/sqrt(n.tlp.PLA),
            m.D.PLA=mean(D.PLA,na.rm=TRUE),n.D.PLA=sum(!is.na(D.PLA)),se.D.PLA=sd(D.PLA,na.rm=T)/sqrt(n.D.PLA),
            m.tlp.PLV=mean(tlp.PLV,na.rm=TRUE),n.tlp.PLV=sum(!is.na(tlp.PLV)),se.tlp.PLV=sd(tlp.PLV,na.rm=T)/sqrt(n.tlp.PLV),
            m.D.PLV=mean(D.PLV,na.rm=TRUE),n.D.PLV=sum(!is.na(D.PLV)),se.D.PLV=sd(D.PLV,na.rm=T)/sqrt(n.D.PLV))
```

## Analysis
```{r}
## PV, stat analysis ####
lm1<-lm(SWCpv~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(rwc.tlp~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(osp.tlp~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(osp.ft~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(em.~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(em~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(af~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(cft~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(ctlp~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(cft.area~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(ctlp.area~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(cft.mass~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(ctlp.mass~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(LMA~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(T.LT~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(LD~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(tlp.PLT~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(D.PLT~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(tlp.PLA~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(D.PLA~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(tlp.PLV~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(D.PLV~Species,data=PVdata)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups


```

# Gas Exchange data
```{r}
### GEx, data loading, variable calculation, means ####

GExdata<-read_xlsx(path = "../data/C3C4 Grasses - GEx.xlsx", sheet = "C3C4G GEx R")#on Marion's PC
GExdata_Zema <- read_excel(path = "../data/AvsPSI_Zema_May2023_Greenhouse_Measurements_4Feb2025updated_MB.xlsx") #Caetano's data

GExdata$Dataset<-factor(GExdata$Dataset)
GExdata$Metabolism<-factor(GExdata$Metabolism)
GExdata$Species<-factor(GExdata$Species,levels=c("Avsa","Hovu","Trae","Pegl","Zema","Chga"))
GExdata$Individual<-factor(GExdata$Individual)
GExdata$Leaf<-factor(GExdata$Leaf)
GExdata$Time.min<-factor(GExdata$Time.min)

# variable calculation
GExdata$FW <- as.numeric(GExdata$FW) 
GExdata$DW <- as.numeric(GExdata$DW)
GExdata$RW <- as.numeric(GExdata$RW)

GExdata$RWC<-(GExdata$FW-GExdata$DW)/(GExdata$RW-GExdata$DW)*100

GExdata$An.area <- as.numeric(GExdata$An.area) 
GExdata$gsw.area <- as.numeric(GExdata$gsw.area) 
GExdata$Ci <- as.numeric(GExdata$Ci) 
GExdata$WUEi <- as.numeric(GExdata$WUEi) 
GExdata$phiPSII <- as.numeric(GExdata$phiPSII) 
GExdata$An.mass.LMApv <- as.numeric(GExdata$An.mass.LMApv) 

# subsets
GExdata.0<-subset(GExdata,Time.min=="0") #combines midday and dehydration time = 0 datasets
GExdata.midd<-subset(GExdata,Dataset=="Midday") #time = 0 
GExdata.dehy<-subset(GExdata,Dataset=="Dehydration") #here time varies from 0 to X minutes

# means GEx midday
m.GExdata.midd<-ddply(GExdata.midd,c("Species","Metabolism"),summarise,
            m.An.area=mean(An.area,na.rm=TRUE),n.An.area=sum(!is.na(An.area)),se.An.area=sd(An.area,na.rm=T)/sqrt(n.An.area),
            m.gsw.area=mean(gsw.area,na.rm=TRUE),n.gsw.area=sum(!is.na(gsw.area)),se.gsw.area=sd(gsw.area,na.rm=T)/sqrt(n.gsw.area),
            m.Ci=mean(Ci,na.rm=TRUE),n.Ci=sum(!is.na(Ci)),se.Ci=sd(Ci,na.rm=T)/sqrt(n.Ci),
            m.WUEi=mean(WUEi,na.rm=TRUE),n.WUEi=sum(!is.na(WUEi)),se.WUEi=sd(WUEi,na.rm=T)/sqrt(n.WUEi),
            m.phiPSII=mean(phiPSII,na.rm=TRUE),n.phiPSII=sum(!is.na(phiPSII)),se.phiPSII=sd(phiPSII,na.rm=T)/sqrt(n.phiPSII))


```
##Analysis

```{r}
## GEx (midday), stat analysis ####
GExdata.midd$An.area <- as.numeric(GExdata.midd$An.area) 
GExdata.midd$gsw.area <- as.numeric(GExdata.midd$gsw.area) 
GExdata.midd$Ci <- as.numeric(GExdata.midd$Ci) 
GExdata.midd$WUEi <- as.numeric(GExdata.midd$WUEi) 
GExdata.midd$phiPSII <- as.numeric(GExdata.midd$phiPSII) 
GExdata.midd$An.mass.LMApv <- as.numeric(GExdata.midd$An.mass.LMApv) 

lm1<-lm(An.area~Species,data=GExdata.midd)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T) #clear assimilation patterns between C3 and C4, with higher A in C4
tuk1$groups

lm1<-lm(gsw.area~Species,data=GExdata.midd)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(Ci~Species,data=GExdata.midd)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(WUEi~Species,data=GExdata.midd)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

lm1<-lm(phiPSII~Species,data=GExdata.midd)
anova(lm1)
tuk1<-HSD.test(lm1,"Species",group=T)
tuk1$groups

GExdata$Dataset<-factor(GExdata$Dataset,levels=c("Midday","Dehydration"))
waterpotential <- ggplot(data= GExdata, aes(x=Species, y=F.wp.leaf, fill= Dataset), alpha = 0.9) +
  geom_boxplot(position=position_dodge(0.8), alpha = 0.9)+
  geom_jitter(position=position_dodge(0.8), alpha = 0.9)+
  annotate("point",y=-1.02,x=1,fill="red",size=5,alpha=0.5,shape=21)+
  annotate("point",y=-1.00,x=2,fill="red",size=5,alpha=0.5,shape=21)+
  annotate("point",y=-1.00,x=3,fill="red",size=5,alpha=0.5,shape=21)+
  annotate("point",y=-0.77,x=4,fill="red",size=5,alpha=0.5,shape=21)+
  annotate("point",y=-0.74,x=5,fill="red",size=5,alpha=0.5,shape=21)+
  annotate("point",y=-0.84,x=6,fill="red",size=5,alpha=0.5,shape=21)+
  scale_fill_manual(values=c("#3734eb", "#eb6134"))+
  scale_color_manual(values=c("#3734eb", "#eb6134"))+
  ylab(expression(paste(Psi[leaf]," (MPa)")))+
  theme_minimal()+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.title.y=element_text(size =13),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13,face="italic"),
        legend.text=element_text(size=12),
        plot.title = element_text(size = 20, hjust = 0.5))+
  guides(fill=guide_legend(title="Condition"))

#waterpotential

#ggsave(filename = "../results/waterpotential_midday_dehydration.jpg", plot = waterpotential, width = 10, height = 6)

#quick graphs
RWC_Phi_species <- ggplot(data= GExdata.dehy, aes(x=RWC, y=F.wp.leaf, colour = Species)) +
  geom_point()+
  theme_minimal()+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_text(size = 13),
        axis.title.y=element_text(size =13),
        legend.text=element_text(size=12),
        legend.position="bottom",
        plot.title = element_text(size = 20, hjust = 0.5))+
  scale_x_continuous(breaks = seq(0,100, by=10)) + 
  ylab(expression(paste(Psi[leaf]," (MPa)")))+
  xlab(expression(paste("Relative water content (%)")))+
  xlim(0,105)
#RWC_Phi_species

#ggsave(filename = "../results/RWC_Phi_dehydration_species.jpg", plot = RWC_Phi_species, width = 6, height = 4)

RWC_Phi_species_wrap <- ggplot(data= GExdata.dehy, aes(x=RWC, y=F.wp.leaf)) +
  geom_point(size=3,shape=21,fill="black",alpha=0.5)+
  facet_wrap(~Species,ncol=3)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13,face="italic"))+
  scale_x_continuous(breaks = seq(0,100, by=10)) + 
  ylab(expression(paste(Psi[leaf]," (MPa)")))+
  xlab(expression(paste("Relative water content (%)")))+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_smooth(aes(x=RWC,y=F.wp.leaf),color="black",fill="grey")+
  #scale_y_continuous(limits=c(-0.25,0.8),breaks=c(0,0.25,0.5,0.75))+
  scale_x_continuous(limits=c(0,100))
  #xlim(0,1)+
  
  
#RWC_Phi_species_wrap

RWC_Phi_meta <- ggplot(data= GExdata.dehy, aes(x=RWC, y=F.wp.leaf, colour = Metabolism)) +
  scale_colour_manual(values=c("#E1BE6A", "#40B0A6"))+
  geom_point()+
  theme_minimal()+
  theme(axis.text.y=element_text(size=13),
        axis.title.x=element_text(size = 13),
        axis.title.y=element_text(size =13),
        legend.text=element_text(size=12),
        legend.position="bottom",
        plot.title = element_text(size = 20, hjust = 0.5))+
  scale_x_continuous(breaks = seq(0,100, by=10)) + 
  ylab(expression(paste(Psi[leaf]," (MPa)")))+
  xlab(expression(paste("Relative water content (%)")))+
  guides(color = guide_legend(nrow = 2, ncol=1))+
  xlim(0,105)
RWC_Phi_meta

#ggsave(filename = "../results/RWC_Phi_dehydration_meta.jpg", plot = RWC_Phi_meta, width = 6, height = 4)

#RWC_Phi_dehydration <- ggarrange(RWC_Phi_species, RWC_Phi_meta, ncol = 2, nrow = 1)
#ggsave(filename = "../results/RWC_Phi_dehydration.jpg", plot = RWC_Phi_dehydration, width = 10, height = 4)

#storage effect
#ca marche pas... excel...
GExdata_storage<-read_xlsx(path = "../data/C3C4 Grasses - GEx.xlsx", sheet = "Midday (Purged)")#on Marion's PC
GExdata_storage<-GExdata_storage[-2,] #remove second unit row

storage <- ggplot(data= GExdata_storage, aes(x=...3, y=leaf)) +
  geom_point()+
  facet_wrap(~...4)+ #Species
  theme_minimal()+
  ylab(expression(paste(Psi[leaf]," (MPa)")))

storage

## GEx (dehydration) #### ?????????????????????????????????
# quick graph for calculating RWC50

g1<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=An.area),size=4,shape=21,fill="red")+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=An.area),color="red",alpha=0.5,fill="tomato1")+
  xlim(0,100)+
  annotate("text",x=10,y=0,label=expression(paste(italic("Chga"))))

# graphs per species ####

# Avsa
Avsa_GEx<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_hline(yintercept=50,color="darkgrey",lty=2)+
  geom_hline(yintercept=100,color="darkgrey",lty=2)+
  geom_vline(xintercept=73.02,color="red",lty=2,lwd=1)+
  geom_vline(xintercept=77.76,color="blue",lty=2,lwd=1)+
  geom_vline(xintercept=46.12,color="green",lty=2,lwd=1)+
  geom_vline(xintercept=89.5,color="black",lty=2,lwd=1)+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Avsa",],aes(x=RWC,y=phiPSII/0.364*100),size=3,shape=21,fill="green",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Avsa",],aes(x=RWC,y=phiPSII/0.364*100),color="green",alpha=0.5,fill="palegreen")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Avsa",],aes(x=RWC,y=An.area/25.20*100),size=3,shape=21,fill="red",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Avsa",],aes(x=RWC,y=An.area/25.20*100),color="red",alpha=0.5,fill="tomato1")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Avsa",],aes(x=RWC,y=gsw.area/0.417*100),size=3,shape=21,fill="blue",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Avsa",],aes(x=RWC,y=gsw.area/0.417*100),color="blue",alpha=0.5,fill="skyblue2")+
  ylim(-25,150)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13),
        legend.title=element_text(),
        title = element_text(size=13, face = "bold.italic"))+
   ggtitle("A. sativa")+
  ylab(expression(paste("relative A"[n],", g"[sw],", ",Phi["PSII"]," (%)")))+
  xlab(expression(paste("RWC (%)")))
  #annotate("text",x=10,y=90,label=expression(paste(italic("Avsa"))))
Avsa_GEx

# Hovu
Hovu_GEx<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_hline(yintercept=50,color="darkgrey",lty=2)+
  geom_hline(yintercept=100,color="darkgrey",lty=2)+
  geom_vline(xintercept=75.78,color="red",lty=2,lwd=1)+
  geom_vline(xintercept=83.95,color="blue",lty=2,lwd=1)+
  geom_vline(xintercept=66.30,color="green",lty=2,lwd=1)+
  geom_vline(xintercept=90.7,color="black",lty=2,lwd=1)+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Hovu",],aes(x=RWC,y=phiPSII/0.385*100),size=3,shape=21,fill="green",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Hovu",],aes(x=RWC,y=phiPSII/0.385*100),color="green",alpha=0.5,fill="palegreen")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Hovu",],aes(x=RWC,y=An.area/28.44*100),size=3,shape=21,fill="red",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Hovu",],aes(x=RWC,y=An.area/28.44*100),color="red",alpha=0.5,fill="tomato1")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Hovu",],aes(x=RWC,y=gsw.area/0.501*100),size=3,shape=21,fill="blue",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Hovu",],aes(x=RWC,y=gsw.area/0.501*100),color="blue",alpha=0.5,fill="skyblue2")+
  ylim(-25,150)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13),
        legend.title=element_blank(),
         title = element_text(size=13, face = "bold.italic"))+
   ggtitle("H. vulgare")+
  ylab(expression(paste("relative A"[n],", g"[sw],", ",Phi["PSII"]," (%)")))+
  xlab(expression(paste("RWC (%)")))
  #annotate("text",x=10,y=90,label=expression(paste(italic("Hovu"))))
Hovu_GEx

# Trae
Trae_GEx<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_hline(yintercept=50,color="darkgrey",lty=2)+
  geom_hline(yintercept=100,color="darkgrey",lty=2)+
  geom_vline(xintercept=73.37,color="red",lty=2,lwd=1)+
  geom_vline(xintercept=81.31,color="blue",lty=2,lwd=1)+
  geom_vline(xintercept=61.15,color="green",lty=2,lwd=1)+
  geom_vline(xintercept=90.0,color="black",lty=2,lwd=1)+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Trae",],aes(x=RWC,y=phiPSII/0.358*100),size=3,shape=21,fill="green",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Trae",],aes(x=RWC,y=phiPSII/0.358*100),color="green",alpha=0.5,fill="palegreen")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Trae",],aes(x=RWC,y=An.area/32.91*100),size=3,shape=21,fill="red",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Trae",],aes(x=RWC,y=An.area/32.91*100),color="red",alpha=0.5,fill="tomato1")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Trae",],aes(x=RWC,y=gsw.area/0.699*100),size=3,shape=21,fill="blue",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Trae",],aes(x=RWC,y=gsw.area/0.699*100),color="blue",alpha=0.5,fill="skyblue2")+
  ylim(-25,150)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_text(size=13),
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13),
        legend.title=element_blank(),
        title = element_text(size=13, face = "bold.italic"))+
   ggtitle("T. aestivum")+
  ylab(expression(paste("relative A"[n],", g"[sw],", ",Phi["PSII"]," (%)")))+
  xlab(expression(paste("RWC (%)")))
  #annotate("text",x=10,y=90,label=expression(paste(italic("Trae"))))
Trae_GEx

# Pegl
Pegl_GEx<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_hline(yintercept=50,color="darkgrey",lty=2)+
  geom_hline(yintercept=100,color="darkgrey",lty=2)+
  geom_vline(xintercept=86.94,color="red",lty=2,lwd=1)+
  geom_vline(xintercept=86.16,color="blue",lty=2,lwd=1)+
  geom_vline(xintercept=83.79,color="green",lty=2,lwd=1)+
  geom_vline(xintercept=91.2,color="black",lty=2,lwd=1)+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Pegl",],aes(x=RWC,y=phiPSII/0.350*100),size=3,shape=21,fill="green",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Pegl",],aes(x=RWC,y=phiPSII/0.350*100),color="green",alpha=0.5,fill="palegreen")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Pegl",],aes(x=RWC,y=An.area/40.28*100),size=3,shape=21,fill="red",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Pegl",],aes(x=RWC,y=An.area/40.28*100),color="red",alpha=0.5,fill="tomato1")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Pegl",],aes(x=RWC,y=gsw.area/0.230*100),size=3,shape=21,fill="blue",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Pegl",],aes(x=RWC,y=gsw.area/0.230*100),color="blue",alpha=0.5,fill="skyblue2")+
  ylim(-25,150)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=13),
        axis.title.x=element_text(size=14),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13),
        legend.title=element_blank(),
         title = element_text(size=13, face = "bold.italic"))+
   ggtitle("P. glaucum")+
  ylab(expression(paste("relative A"[n],", g"[sw],", ",Phi["PSII"]," (%)")))+
  xlab(expression(paste("RWC (%)")))
  #annotate("text",x=10,y=90,label=expression(paste(italic("Pegl"))))
Pegl_GEx

# Chga
Chga_GEx<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_hline(yintercept=50,color="darkgrey",lty=2)+
  geom_hline(yintercept=100,color="darkgrey",lty=2)+
  geom_vline(xintercept=80.90,color="red",lty=2,lwd=1)+
  geom_vline(xintercept=82.80,color="blue",lty=2,lwd=1)+
  geom_vline(xintercept=77.47,color="green",lty=2,lwd=1)+
  geom_vline(xintercept=93.1,color="black",lty=2,lwd=1)+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=phiPSII/0.252*100),size=3,shape=21,fill="green",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=phiPSII/0.252*100),color="green",alpha=0.5,fill="palegreen")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=An.area/26.75*100),size=3,shape=21,fill="red",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=An.area/26.75*100),color="red",alpha=0.5,fill="tomato1")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=gsw.area/0.154*100),size=3,shape=21,fill="blue",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Chga",],aes(x=RWC,y=gsw.area/0.154*100),color="blue",alpha=0.5,fill="skyblue2")+
  ylim(-25,150)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_text(size=13),
        axis.title.x=element_text(size=14),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13),
        legend.title=element_blank(),
        title = element_text(size=13, face = "bold.italic"))+
   ggtitle("C. gayan")+
  ylab(expression(paste("relative A"[n],", g"[sw],", ",Phi["PSII"]," (%)")))+
  xlab(expression(paste("RWC (%)")))
  #annotate("text",x=10,y=90,label=expression(paste(italic("Chga"))))

# Zema
Zema_GEx<-ggplot()+
  geom_hline(yintercept=0,color="darkgrey")+
  geom_vline(xintercept=0,color="darkgrey")+
  geom_hline(yintercept=50,color="darkgrey",lty=2)+
  geom_hline(yintercept=100,color="darkgrey",lty=2)+
  geom_vline(xintercept=80.90,color="red",lty=2,lwd=1)+
  geom_vline(xintercept=82.80,color="blue",lty=2,lwd=1)+
  geom_vline(xintercept=77.47,color="green",lty=2,lwd=1)+
  geom_vline(xintercept=93.1,color="black",lty=2,lwd=1)+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Zema",],aes(x=RWC,y=phiPSII/0.252*100),size=3,shape=21,fill="green",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Zema",],aes(x=RWC,y=phiPSII/0.252*100),color="green",alpha=0.5,fill="palegreen")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Zema",],aes(x=RWC,y=An.area/26.75*100),size=3,shape=21,fill="red",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Zema",],aes(x=RWC,y=An.area/26.75*100),color="red",alpha=0.5,fill="tomato1")+
  geom_point(data=GExdata.dehy[GExdata.dehy$Species=="Zema",],aes(x=RWC,y=gsw.area/0.154*100),size=3,shape=21,fill="blue",alpha=0.5)+
  geom_smooth(data=GExdata.dehy[GExdata.dehy$Species=="Zema",],aes(x=RWC,y=gsw.area/0.154*100),color="blue",alpha=0.5,fill="skyblue2")+
  ylim(-25,150)+
  xlim(0,100)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_text(size=13),
        axis.title.x=element_text(size=14),
        axis.text.x=element_text(angle=0,vjust=1,hjust=0.5,size=13),
        legend.title=element_blank(),
        title = element_text(size=13, face = "bold.italic"))+
   ggtitle("Z. mays")+
  ylab(expression(paste("relative A"[n],", g"[sw],", ",Phi["PSII"]," (%)")))+
  xlab(expression(paste("RWC (%)")))

Zema_GEx

### all plots ----
GEx_plot <- ggarrange(Avsa_GEx, Hovu_GEx, Trae_GEx, Pegl_GEx, Zema_GEx, Chga_GEx, ncol =3, nrow = 2)

GEx_plot 

ggsave(filename = "../results/GEx_plot .jpg", plot = GEx_plot, width = 12, height = 8)
```

# X50 data

```{r}
X50data<-read_xlsx("../data/C3C4 Grasses - Xrwc50 data.xlsx",sheet = "C3C4G X50 R" )

    
X50data$WaterStatus<-factor(X50data$WaterStatus)
X50data$Species<-factor(X50data$Species,levels=c("Avsa","Hovu","Trae","Pegl","Zema","Chga"))
X50data$Metabolism<-factor(X50data$Metabolism)

# subsets
X50data.RWC<-subset(X50data,WaterStatus=="RWC")

```

##Analysis
```{r}
## X50, correlations ####
d1<-X50data.RWC[c("LMA","LT","LD","LDMC","RWCtlp",
                "An50","gsw50","phiPSII50","dehyF0.6","dehyF0.35","PLRC10","PLRC25",
                "PLT10","PLT25","PLTdry","PLA10","PLA25","PLAdry","PLV10","PLV25","PLVdry")]

d1$An50<- as.numeric(d1$An50)
d1$gsw50<- as.numeric(d1$gsw50)
d1$phiPSII50 <-as.numeric(d1$phiPSII50)

m1<-cor(d1,use="pairwise.complete.obs")

g1<-corrplot.mixed(m1)
# most interesting, clear relationships
# RWC,dehyF0.35 vs RWC,PLV25
g1<-ggplot(X50data.RWC,aes(x=PLV25,y=dehyF0.35))+
  geom_abline(intercept=0,slope=1,colour="darkgrey")+
  geom_smooth(size=1,alpha=0.8,method=lm,se=T,colour="darkgrey",fill="lightgrey")+
  geom_point(size=3,aes(colour=Metabolism,shape=Species))+
  scale_shape_manual(values=c(16,15,17,16,15,17))+
  ylim(-5,55)+
  xlim(60,85)+
  #geom_hline(yintercept=0,lty=2)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  ylab(expression(paste("RWC"["dehyF=0.35"]," (%)")))+
  xlab(expression(paste("RWC"["PLV=25"]," (%)")))
g1
# stat
lm1<-lm(dehyF0.35~PLV25,data=X50data.RWC)
anova(lm1)
summary(lm1)
# RWC,dehyF0.60 vs RWC,PLA25
g1<-ggplot(X50data.RWC,aes(x=PLA25,y=dehyF0.6))+
  geom_abline(intercept=0,slope=1,colour="darkgrey")+
  geom_smooth(size=1,alpha=0.8,method=lm,se=T,colour="darkgrey",fill="lightgrey")+
  geom_point(size=3,aes(colour=Metabolism,shape=Species))+
  scale_shape_manual(values=c(16,15,17,16,15,17))+
  ylim(10,65)+
  xlim(25,45)+
  #geom_hline(yintercept=0,lty=2)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  ylab(expression(paste("RWC"["dehyF=0.6"]," (%)")))+
  xlab(expression(paste("RWC"["PLA=25"]," (%)")))
g1
# stat
lm1<-lm(dehyF0.6~PLA25,data=X50data.RWC)
anova(lm1)
summary(lm1)
# RWC,PLT25 vs LDMC
g1<-ggplot(X50data.RWC,aes(x=LDMC,y=PLT25))+
  geom_abline(intercept=0,slope=1,colour="darkgrey")+
  geom_smooth(size=1,alpha=0.8,method=lm,se=T,colour="darkgrey",fill="lightgrey")+
  geom_point(size=3,aes(colour=Metabolism,shape=Species))+
  scale_shape_manual(values=c(16,15,17,16,15,17))+
  ylim(40,85)+
  xlim(0.075,0.175)+
  #geom_hline(yintercept=0,lty=2)+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        axis.title.y=element_text(size=13),
        axis.text.y=element_text(size=12),
        axis.title.x=element_text(size=13),
        axis.text.x=element_text(size=12),
        legend.title=element_blank(),
        legend.text=element_text(size=12),
        legend.key.width=unit(2,'cm'))+
  ylab(expression(paste("RWC"["PLT=25"]," (%)")))+
  xlab(expression(paste("LDMC (g g"^-1,")")))
# stat
lm1<-lm(PLT25~LDMC,data=X50data.RWC)
anova(lm1)
summary(lm1)

## X50, PCA ####
# complete obs
d1<-X50data.RWC[c("Species","Metabolism",
                  "dehyF0.6","dehyF0.35","PLRC10","PLRC25",
                  "PLT10","PLT25","PLTdry","PLA10","PLA25","PLAdry","PLV10","PLV25","PLVdry")]
pc1<-prcomp(scale(d1[c(3:15)]))
met<-as.factor(d1$Metabolism[1:6])
sp<-as.factor(d1$Species[1:6])
# 
pca1<-fviz_pca_biplot(pc1,label="var",col.var="black",repel=T,
                      geom.ind="point",pointsize=5,col.ind=met,invisible="quali")+
  theme_bw()+
  theme(panel.grid.minor=element_blank(),
        panel.grid.major=element_blank(),
        panel.border=element_rect(size=1,colour="#222222"),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10),
        axis.title.x=element_text(size=14),
        axis.title.y=element_text(size=14),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_text(size=10),
        legend.background=element_blank(),
        title=element_blank())+
  ylab(expression(paste("PC2 (28.7 %)")))+
  xlab(expression(paste("PC1 (54.1 %)")))

pca1
```


